---
title: "Swing trader"
format:
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
    theme: cosmo
    nav-buttons:
      - icon: github
        href: https://github.com/seamusrobertmurphy/swing-trader
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(jsonlite); library(ggplot2); library(dplyr); library(scales); library(DT)

# Find the repo root by walking up until inputs/ appears, so this renders the
# same from the repo root, from dashboard/, or from anywhere a scheduler puts
# its working directory. DAYTRADER_DATA overrides it outright.
find_repo <- function(start = getwd()) {
  p <- normalizePath(start, mustWork = FALSE)
  for (i in 1:6) {
    if (dir.exists(file.path(p, "inputs"))) return(p)
    parent <- dirname(p); if (parent == p) break; p <- parent
  }
  stop("cannot locate the repo root from ", start)
}
data_path <- Sys.getenv("DAYTRADER_DATA",
                        file.path(find_repo(), "outputs", "dashboard", "data.json"))
if (!file.exists(data_path))
  stop("no data at ", data_path, " -- run: .venv/bin/python inputs/dashboard_data.py")
d <- fromJSON(data_path, simplifyVector = TRUE)
if (!length(d$headline)) stop("data.json has no headline block; the emitter failed")

h <- d$headline; m <- d$meta

pct  <- function(x, dp = 2) sprintf(paste0("%+.", dp, "f%%"), 100 * x)
usd  <- function(x) paste0("$", formatC(x, format = "f", big.mark = ",", digits = 0))
good <- "#1a7f4e"; bad <- "#b3261e"; warn <- "#a1650a"; ink <- "#1f2328"
tone <- function(x) if (is.na(x)) "secondary" else if (x >= 0) "success" else "danger"

theme_book <- theme_minimal(base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold", size = 12),
        plot.subtitle = element_text(colour = "grey35", size = 10),
        axis.title = element_text(colour = "grey35", size = 9))
```

# Where the money is

## Row {height="18%"}

```{r}
#| content: valuebox
#| title: "Account value"
list(icon = "wallet2", color = tone(h$since_live),
     value = usd(h$equity))
```

```{r}
#| content: valuebox
#| title: "Since it went live"
list(icon = if (h$since_live >= 0) "graph-up" else "graph-down",
     color = tone(h$since_live), value = pct(h$since_live))
```

```{r}
#| content: valuebox
#| title: "The market, same days"
list(icon = "bank", color = "light",
     value = if (is.null(h$spy_since_live)) "n/a" else pct(h$spy_since_live))
```

```{r}
#| content: valuebox
#| title: "Cost per trade vs the 5-10 assumed"
list(icon = "cash-coin",
     color = if (!length(d$slippage)) "secondary"
             else if (tail(d$slippage$mean_bp, 1) <= 10) "success" else "danger",
     value = if (!length(d$slippage)) "no trades"
             else paste0(sprintf("%.1f", tail(d$slippage$mean_bp, 1)), " bp"))
```

```{r}
#| content: valuebox
#| title: "Clean cycles done"
list(icon = "arrow-repeat",
     color = if (d$cycles$done >= d$cycles$needed) "success" else "warning",
     value = paste0(d$cycles$done, " of ", d$cycles$needed))
```

## Row {height="12%"}

::: {.card title="What this page is"}
**This is fake money.** It is a paper account and the switch that would let it
spend real money is off.

`r m$mark_note` Marked `r m$generated_at_pretty`.
The book has been running `r m$sessions` trading sessions.
Was this move within expectations? **`r if (h$within_expectations) "Yes" else "No"`** —
the plan expected swings of about `r sprintf("%.1f%%", 100*h$expected_swing)` over
that stretch, and this is `r sprintf("%.1f", abs(h$sigmas))` times that.
:::

## Row {height="45%"}

### Column {width="62%"}

```{r}
#| title: "The book against the market, both starting at $100,000"
eq <- d$equity_curve |> mutate(date = as.Date(date), who = "The book")
bm <- if (length(d$benchmark$series)) {
  d$benchmark$series |> mutate(date = as.Date(date),
                              who = paste0("The market (", d$benchmark$symbol, ")"))
} else eq[0, ]
both <- bind_rows(eq, bm)

ggplot(both, aes(date, equity, colour = who)) +
  geom_hline(yintercept = 100000, linetype = "dotted", colour = "grey55") +
  geom_line(linewidth = 0.9) +
  geom_point(data = filter(both, date == max(date)), size = 2) +
  scale_colour_manual(values = setNames(c(ink, "grey60"), unique(both$who))) +
  scale_y_continuous(labels = dollar_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, colour = NULL,
       subtitle = "Dotted line is the starting stake. Above it is a profit.") +
  theme_book + theme(legend.position = "top")
```

### Column {width="38%"}

```{r}
#| title: "Is it one bet or fifty?"
cc <- d$concentration
if (isTRUE(cc$available)) {
  g <- cc$groups |> mutate(rank = row_number(),
                           label = paste0(n, ifelse(n == 1, " stock", " stocks")))
  ggplot(g, aes(reorder(label, weight), weight)) +
    geom_col(fill = ifelse(g$weight > cc$cap, bad, good), width = 0.7) +
    geom_hline(yintercept = cc$cap, linetype = "dashed", colour = ink) +
    annotate("text", x = 0.8, y = cc$cap, vjust = -0.7, hjust = 0, size = 3.1,
             colour = ink, label = paste0("your ", percent(cc$cap, 1), " limit")) +
    coord_flip() +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Each bar is a group of stocks that move together.\n",
                           "Red means the group is bigger than your rules allow.")) +
    theme_book
} else {
  ggplot() + annotate("text", 0, 0, label = "not computable") + theme_void()
}
```

## Row {height="25%"}

::: {.card title="What the concentration bar means"}
```{r}
#| output: asis
cc <- d$concentration
if (isTRUE(cc$available)) {
  cat(sprintf(
"The biggest group of stocks that move together is **%d of the %d holdings**, worth
**%s of the money**. Your rules cap any such group at %s.

Momentum concentrates on purpose: last year's winners are last year's winning
industry. That is why the book can lose six percent in a week the market barely
moves, and win it back the next day. Both are the same fact.

Right now **%d holding%s sit%s over the cap**, worst is %s at %s.\n\n",
    cc$biggest_group_names, h$positions, percent(cc$biggest_group_weight, 0.1),
    percent(cc$cap, 1), cc$over_cap, ifelse(cc$over_cap == 1, "", "s"),
    ifelse(cc$over_cap == 1, "s", ""), cc$worst_local_symbol,
    percent(cc$worst_local_weight, 0.1)))
}
```
:::

# What it costs to trade

## Row {height="50%"}

```{r}
#| title: "Cost per trade, each rebalance, against what we assumed"
if (length(d$slippage)) {
  s <- d$slippage |> mutate(cycle = as.Date(cycle))
  ggplot(s, aes(cycle)) +
    annotate("rect", xmin = min(s$cycle) - 1, xmax = max(s$cycle) + 1,
             ymin = s$model_low[1], ymax = s$model_high[1],
             fill = good, alpha = 0.14) +
    geom_segment(aes(xend = cycle, y = 0, yend = mean_bp), colour = "grey70") +
    geom_point(aes(y = mean_bp, colour = mean_bp > model_high), size = 4) +
    geom_point(aes(y = median_bp), shape = 21, fill = "white", size = 2.6) +
    geom_text(aes(y = mean_bp, label = sprintf("%.1f", mean_bp)),
              vjust = -1.1, size = 3.3) +
    scale_colour_manual(values = c(`TRUE` = bad, `FALSE` = good), guide = "none") +
    labs(x = NULL, y = "basis points per fill",
         subtitle = paste0("Filled dot is the average, hollow dot the typical trade.\n",
                           "Green band is the 5 to 10 basis points we assumed. ",
                           "One basis point is a hundredth of one percent.")) +
    theme_book
} else {
  ggplot() + annotate("text", 0, 0, label = "no trades yet") + theme_void()
}
```

## Row {height="50%"}

::: {.card title="Why the second one was expensive"}
```{r}
#| output: asis
if (length(d$slippage)) {
  s <- tail(d$slippage, 1)
  cat(sprintf(
"The most recent rebalance was **%d fills** costing **%.1f basis points on average**,
and **%.1f for the typical one**. In money that is %s on %s traded.

**%d of those %d fills landed in the first fifteen minutes of the day.** That is
the cause. The opening bell has the widest gap between what buyers offer and
sellers ask, and prices move fastest. The orders were sent overnight, and orders
sent to a shut exchange all execute the instant it opens.

The fix is in the code: it now refuses to send orders outside trading hours. The
first rebalance, sent mid-morning, cost 3.8 basis points.\n\n",
    s$fills, s$mean_bp, s$median_bp,
    paste0("$", formatC(s$dollars, format = "f", digits = 0, big.mark = ",")),
    paste0("$", formatC(s$notional, format = "f", digits = 0, big.mark = ",")),
    s$at_open, s$fills))
}
```
:::

# What we own

## Row

```{r}
#| title: "Every holding, worst first"
p <- d$positions |>
  transmute(Symbol = symbol,
            Value = value,
            `Share of book` = weight,
            `Gain or loss` = plpc,
            `In dollars` = pl)
datatable(p, rownames = FALSE, options = list(pageLength = 15, dom = "tip"),
          class = "compact stripe hover") |>
  formatCurrency("Value", digits = 0) |>
  formatCurrency("In dollars", digits = 0) |>
  formatPercentage("Share of book", 2) |>
  formatPercentage("Gain or loss", 1) |>
  formatStyle("Gain or loss",
              color = styleInterval(0, c("#b3261e", "#1a7f4e")),
              fontWeight = "bold")
```

# Are the rules holding

## Row

```{r}
#| title: "Every safety rule, and whether it is holding right now"
g <- d$guards |> transmute(Rule = name, `In plain words` = plain,
                          Status = state, `Right now` = value, Detail = detail)
datatable(g, rownames = FALSE, options = list(dom = "t", pageLength = 20),
          class = "compact stripe") |>
  formatStyle("Status", fontWeight = "bold",
              color = styleEqual(c("OK", "DRIFT", "BREACH", "TRIPPED", "FIRING"),
                                 c("#1a7f4e", "#a1650a", "#b3261e", "#b3261e", "#b3261e")))
```

## Row {height="30%"}

::: {.card title="How far through the test we are"}
```{r}
#| output: asis
cy <- d$cycles
cat(sprintf(
"This is a paper trial with one job: find out whether real trading costs match
what the strategy assumed. That takes about **%d clean weekly rebalances**, and
**%d** are done.

", cy$needed, cy$done))
if (length(cy$late) && cy$late > 0) {
  cat(sprintf("%d ran late. The longest gap between two was **%d days** against the
7 the weekly cadence intends.\n\n", length(cy$late), cy$worst_gap))
} else {
  cat("None have run late so far.\n\n")
}
cat("Until the trial finishes, nothing here says the strategy works with real
money. It says the plumbing does.\n")
```
:::
