---
title: "Swing trader"
format:
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
    theme: [darkly, dashboard.scss]
    nav-buttons:
      - icon: github
        href: https://github.com/seamusrobertmurphy/swing-trader
execute:
  echo: false
  warning: false
  message: false
# Nine candlestick panels at knitr's default resolution pushed the standalone
# page past ten megabytes, which is slow to open over a phone connection for no
# gain: nothing here is read at print resolution.
knitr:
  opts_chunk:
    dev: png
    dpi: 96
---

```{r setup}
library(jsonlite); library(ggplot2); library(dplyr); library(tidyr)
library(scales); library(DT); library(patchwork)

# Find the repo root by walking up until inputs/ appears, so this renders the
# same from the repo root, from dashboard/, or from anywhere a scheduler puts
# its working directory. DAYTRADER_DATA overrides it outright.
find_repo <- function(start = getwd()) {
  p <- normalizePath(start, mustWork = FALSE)
  for (i in 1:6) {
    if (dir.exists(file.path(p, "inputs"))) return(p)
    parent <- dirname(p); if (parent == p) break; p <- parent
  }
  stop("cannot locate the repo root from ", start)
}
data_path <- Sys.getenv("DAYTRADER_DATA",
                        file.path(find_repo(), "outputs", "dashboard", "data.json"))
if (!file.exists(data_path))
  stop("no data at ", data_path, " -- run: .venv/bin/python inputs/dashboard_data.py")
d <- fromJSON(data_path, simplifyVector = TRUE)
if (!length(d$headline)) stop("data.json has no headline block; the emitter failed")

h <- d$headline; m <- d$meta

# ---- palette -------------------------------------------------------------
# The same eight colours the stylesheet uses. Defined once here so a red in a
# chart is the same red as a red in a table.
bg   <- "#0d1117"; card <- "#161b22"
ink  <- "#e6edf3"; mute <- "#8b98a9"; grid <- "#242c36"
good <- "#2ea86b"; bad  <- "#e5534b"; warn <- "#d29922"; accent <- "#58a6ff"
neut <- "#6e7b8b"
# A categorical set that stays distinguishable on a dark ground and does not
# rely on red-green separation, which is the pair a colour-blind reader loses.
cats <- c("#58a6ff", "#2ea86b", "#d29922", "#bc8cff", "#39c5cf", "#e5534b",
          "#f78166", "#8ddb8c", "#a5a5f5", "#c9a227", "#7ee787", "#ff9bce",
          "#6e7b8b")

# An ISO stamp puts a T where a space belongs, which in a table reads as a typo.
when <- function(x, n = 19) sub("T", " ", substr(x, 1, n))

pct  <- function(x, dp = 2) ifelse(is.na(x), "n/a", sprintf(paste0("%+.", dp, "f%%"), 100 * x))
# formatC puts the minus inside the dollars ("$-1,484"), which reads as a
# typo rather than a loss.
usd  <- function(x) paste0(ifelse(x < 0, "-$", "$"),
                           formatC(abs(x), format = "f", big.mark = ",", digits = 0))
tone <- function(x) if (is.null(x) || is.na(x)) "secondary" else if (x >= 0) "success" else "danger"

# jsonlite hands back NULL for an absent block and a list for an empty array.
# Every panel below asks through this, so one missing feed blanks one card
# instead of failing the whole page.
`%||%` <- function(a, b) if (is.null(a) || length(a) == 0) b else a

tbl <- function(x) {
  if (is.null(x) || length(x) == 0) return(data.frame())
  if (is.data.frame(x)) return(x)
  as.data.frame(x, stringsAsFactors = FALSE)
}
blank <- function(msg) {
  ggplot() + annotate("text", 0, 0, label = msg, colour = mute, size = 4) +
    theme_void() + theme(plot.background = element_rect(fill = card, colour = NA))
}

theme_dark_book <- theme_minimal(base_size = 11) +
  theme(
    plot.background  = element_rect(fill = card, colour = NA),
    panel.background = element_rect(fill = card, colour = NA),
    legend.background = element_rect(fill = card, colour = NA),
    legend.key = element_rect(fill = card, colour = NA),
    panel.grid.major = element_line(colour = grid, linewidth = 0.3),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    text = element_text(colour = ink),
    axis.text = element_text(colour = mute, size = 8.5),
    axis.title = element_text(colour = mute, size = 8.5),
    legend.text = element_text(colour = mute, size = 8.5),
    strip.text = element_text(colour = ink, face = "bold", size = 9),
    plot.title.position = "plot",
    plot.title = element_text(face = "bold", size = 11, colour = ink),
    plot.subtitle = element_text(colour = mute, size = 8.8, lineheight = 1.15))
theme_set(theme_dark_book)

# A pie forces a square panel, so the drawing does not fill the width it was
# given and the leftover strip shows the drawing device's own background. That
# background is white by default, which on a dark page reads as two blank
# columns beside every pie. Set it once, for every chart on the page.
knitr::opts_chunk$set(dev.args = list(bg = card))

dark_dt <- function(x, ...) {
  datatable(x, rownames = FALSE, class = "compact stripe hover", ...)
}
```

# Money

## Row {height="15%"}

```{r}
#| content: valuebox
#| title: "Account value"
list(icon = "wallet2", color = tone(h$since_live), value = usd(h$equity))
```

```{r}
#| content: valuebox
#| title: "Since it went live"
list(icon = if (h$since_live >= 0) "graph-up" else "graph-down",
     color = tone(h$since_live), value = pct(h$since_live))
```

```{r}
#| content: valuebox
#| title: "The market, same days"
list(icon = "bank", color = "light",
     value = if (is.null(h$spy_since_live)) "n/a" else pct(h$spy_since_live))
```

```{r}
#| content: valuebox
#| title: "Ahead of or behind the market"
list(icon = "flag", color = tone(h$excess),
     value = if (is.null(h$excess)) "n/a" else pct(h$excess))
```

```{r}
#| content: valuebox
#| title: "Down from its best day"
list(icon = "arrow-down-right",
     color = if (h$from_peak > -0.05) "light" else "warning",
     value = pct(h$from_peak))
```

```{r}
#| content: valuebox
#| title: "Cost per trade vs the 5-10 assumed"
sl <- tbl(d$slippage)
list(icon = "cash-coin",
     color = if (!nrow(sl)) "secondary"
             else if (tail(sl$mean_bp, 1) <= 10) "success" else "danger",
     value = if (!nrow(sl)) "no trades"
             else paste0(sprintf("%.1f", tail(sl$mean_bp, 1)), " bp"))
```

```{r}
#| content: valuebox
#| title: "Clean cycles done"
list(icon = "arrow-repeat",
     color = if (d$cycles$done >= d$cycles$needed) "success" else "warning",
     value = paste0(d$cycles$done, " of ", d$cycles$needed))
```

## Row {height="10%"}

::: {.card title="What this page is"}
**This is fake money.** It is a paper account and the switch that would let it
spend real money is off.

`r m$mark_note` Marked `r m$generated_at_pretty`.
The book has been running `r m$sessions` trading sessions and holds
`r h$positions` stocks with `r sprintf("%.1f%%", 100*h$cash_pct)` in cash.
Was this move within expectations? **`r if (h$within_expectations) "Yes" else "No"`** —
the plan expected swings of about `r sprintf("%.1f%%", 100*h$expected_swing)` over
that stretch, and this is `r sprintf("%.1f", abs(h$sigmas))` times that.
:::

## Row {height="38%"}

### Column {width="62%"}

```{r}
#| title: "The book against the market, both starting at $100,000"
live <- as.Date(d$meta$live_from)
eq <- tbl(d$equity_curve) |> mutate(date = as.Date(date)) |>
      filter(date >= live) |> mutate(who = "The book")
bm <- if (length(d$benchmark$series)) {
  tbl(d$benchmark$series) |> mutate(date = as.Date(date),
      who = paste0("The market (", d$benchmark$symbol, ")"))
} else eq[0, ]
both <- bind_rows(eq, bm)

ggplot(both, aes(date, equity, colour = who)) +
  geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
  geom_line(linewidth = 0.9) +
  geom_point(data = filter(both, date == max(date)), size = 2.2) +
  scale_colour_manual(values = setNames(c(accent, neut), unique(both$who))) +
  scale_y_continuous(labels = dollar_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, colour = NULL,
       subtitle = "Dotted line is the starting stake. Above it is a profit.") +
  theme(legend.position = "top")
```

### Column {width="38%"}

```{r}
#| title: "How far below its best the account has been"
dd <- tbl(d$risk$drawdown)
if (nrow(dd)) {
  dd <- dd |> mutate(date = as.Date(date)) |> filter(date >= live)
  ggplot(dd, aes(date, dd)) +
    geom_area(fill = bad, alpha = 0.28) +
    geom_line(colour = bad, linewidth = 0.7) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Zero means it is at a new high. The deepest hole so far\n",
                           "was ", percent(d$risk$worst_dd, 0.1),
                           ". A 25% fall on any one stock sells it automatically.")) 
} else blank("not enough history yet")
```

## Row {height="37%"}

### Column {width="34%"}

```{r}
#| title: "What each day did"
dl <- tbl(d$risk$daily)
if (nrow(dl)) {
  dl <- dl |> mutate(date = as.Date(date)) |> filter(date >= live)
  ggplot(dl, aes(date, ret, fill = ret >= 0)) +
    geom_col(width = 0.6) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("One bar per trading day. ", d$risk$up_days, " up, ",
                           d$risk$down_days, " down. Best ",
                           percent(d$risk$best_day, 0.1), ", worst ",
                           percent(d$risk$worst_day, 0.1), "."))
} else blank("no full days yet")
```

### Column {width="34%"}

```{r}
#| title: "Today and the last few sessions, minute by minute"
it <- tbl(d$intraday)
if (nrow(it) > 2) {
  it <- it |> mutate(t = as.POSIXct(t, format = "%Y-%m-%dT%H:%M:%S", tz = "America/New_York"))
  ggplot(it, aes(t, equity)) +
    geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
    geom_line(colour = accent, linewidth = 0.6) +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Marked every 15 minutes while the market is open.\n",
                           "The flat stretches are nights and weekends, removed."))
} else blank("no intraday marks")
```

### Column {width="32%"}

```{r}
#| title: "How rough the ride is"
rv <- tbl(d$risk$rolling_vol)
if (nrow(rv) > 2) {
  rv <- rv |> mutate(date = as.Date(date))
  ggplot(rv, aes(date, vol)) +
    geom_hline(yintercept = 0.35, linetype = "dashed", colour = warn) +
    geom_line(colour = accent, linewidth = 0.8) +
    scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, NA)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("How much the account swings, stated as a year's worth.\n",
                           "Dashed line is the 35% the plan expected. Higher is rougher."))
} else blank("needs ten sessions before this means anything")
```

# What we own

## Row {height="30%"}

```{r}
#| title: "By what it moves with"
#| fig-width: 4.2
#| fig-height: 5.4
# One drawing routine for all four pies. A slice's share is written into its
# own legend entry rather than onto the slice, because at four pies to a row
# the thin slices have no room for a label and the reader ends up guessing.
donut <- function(df, palette = cats, order_by = "weight") {
  if (!nrow(df)) return(blank("nothing to show"))
  if (order_by == "weight") df <- df |> arrange(desc(weight))
  df <- df |> mutate(key = paste0(label, "   ", percent(weight, 0.1)),
                     key = factor(key, levels = key))
  ggplot(df, aes(x = 2, y = weight, fill = key)) +
    geom_col(width = 1, colour = card, linewidth = 0.5) +
    coord_polar(theta = "y") +
    xlim(0.4, 2.5) +
    scale_fill_manual(values = setNames(palette[seq_len(nrow(df))], levels(df$key)),
                      name = NULL) +
    theme_void(base_size = 9) +
    theme(plot.background = element_rect(fill = card, colour = NA),
          legend.background = element_rect(fill = card, colour = NA),
          legend.key.size = unit(11, "pt"),
          legend.text = element_text(colour = ink, size = 8.6),
          legend.position = "bottom",
          legend.direction = "vertical",
          legend.justification = "left",
          plot.margin = margin(2, 2, 2, 2))
}
donut(tbl(d$mix$sector))
```

```{r}
#| title: "By groups that move together"
#| fig-width: 4.2
#| fig-height: 5.4
donut(tbl(d$mix$cluster))
```

```{r}
#| title: "By how each holding is doing"
#| fig-width: 4.2
#| fig-height: 5.4
mv <- tbl(d$mix$move)
ord <- c("Down more than 10%", "Down 2 to 10%", "Roughly flat",
         "Up 2 to 10%", "Up more than 10%")
if (nrow(mv)) {
  mv <- mv |> mutate(label = factor(label, levels = ord)) |> arrange(label)
  donut(mv, palette = c(bad, "#b4514c", neut, "#3f9a67", good)[
    match(as.character(mv$label), ord)], order_by = "given")
} else blank("no holdings")
```

```{r}
#| title: "Where the shares are listed"
#| fig-width: 4.2
#| fig-height: 5.4
donut(tbl(d$mix$venue))
```

## Row {height="12%"}

::: {.card title="What the four pies are cutting"}
Same money, four ways of slicing it, because any one slice flatters and the
disagreement between them is the point. **What it moves with** files each
holding under the sector fund whose daily moves it has most closely followed
over the past year; there is no sector list in this repo, so this is a
measurement, not a label. **Groups that move together** is stricter: it joins
any two holdings whose daily moves agree more than `r percent(d$concentration$rho, 1)`
of the time, and your rules cap one such group at `r percent(d$concentration$cap, 1)`.
**How each holding is doing** measures against what we paid, a number used
nowhere else except the automatic 25% sell. **Where the shares are listed** is
the exchange, worth a glance because a thin exchange is a slower and dearer exit.
:::

## Row {height="30%"}

### Column {width="55%"}

```{r}
#| title: "Which holdings moved the whole account, in percentage points"
at <- tbl(d$attribution)
if (nrow(at)) {
  top <- bind_rows(head(at, 8), tail(at, 8)) |> distinct(symbol, .keep_all = TRUE) |>
    arrange(points) |> mutate(symbol = factor(symbol, levels = symbol))
  ggplot(top, aes(symbol, points, fill = points >= 0)) +
    geom_col(width = 0.7) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    geom_text(aes(label = sprintf("%+.2f", points),
                  hjust = ifelse(points >= 0, -0.15, 1.15)), size = 2.9, colour = ink) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    coord_flip(clip = "off") +
    scale_y_continuous(expand = expansion(mult = c(0.14, 0.14))) +
    labs(x = NULL, y = "percentage points of the whole account",
         subtitle = paste0("A stock down 20% at a 1.5% weight costs the book 0.3 points.\n",
                           "This ranks by the damage done, not by the stock's own fall."))
} else blank("no holdings")
```

### Column {width="45%"}

```{r}
#| title: "Is it one bet or fifty?"
cc <- d$concentration
if (isTRUE(cc$available)) {
  g   <- tbl(cc$groups)
  big <- g[g$n > 1, , drop = FALSE]
  ones<- g[g$n == 1, , drop = FALSE]
  rows <- data.frame(
    key    = as.character(big$rank),
    label  = paste0(big$n, " stocks that move together"),
    weight = big$weight, ord = big$weight, lone = FALSE, stringsAsFactors = FALSE)
  if (nrow(ones) > 0) {
    rows <- rbind(rows, data.frame(
      key    = "loners",
      label  = paste0(nrow(ones), " stocks on their own"),
      weight = sum(ones$weight), ord = -1, lone = TRUE, stringsAsFactors = FALSE))
  }
  # Two groups of the same size carry the same words, and the words were the
  # axis identity, so factor() hit a duplicated level and the whole page failed
  # to render (2026-08-27: three groups of two after the cluster-cap rebalance).
  # The group rank is the identity now; the words are only the printed label.
  rows$key <- factor(rows$key, levels = rows$key[order(rows$ord)])

  ggplot(rows, aes(key, weight)) +
    geom_col(aes(fill = !lone & weight > cc$cap), width = 0.68) +
    geom_hline(yintercept = cc$cap, linetype = "dashed", colour = ink) +
    geom_text(aes(label = percent(weight, 0.1)), hjust = -0.15, size = 3, colour = ink) +
    scale_fill_manual(values = c(`TRUE` = bad, `FALSE` = good), guide = "none") +
    coord_flip(clip = "off") +
    scale_x_discrete(labels = setNames(rows$label, as.character(rows$key))) +
    scale_y_continuous(labels = percent_format(accuracy = 1),
                       expand = expansion(mult = c(0, 0.16))) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Dashed line is your ", percent(cc$cap, 1),
                           " limit. Red is over it.\n",
                           "The bottom bar is every holding that moves with ",
                           "nothing else you own.")) +
    theme(plot.margin = margin(6, 26, 6, 6))
} else blank("not computable")
```

## Row {height="28%"}

```{r}
#| title: "Every holding, worst first"
p <- tbl(d$positions)
sm <- tbl(d$mix$detail)
p$moves_with <- NA_character_
if (nrow(sm) && "sector" %in% names(sm))
  p$moves_with <- sm$sector[match(p$symbol, sm$symbol)]
p <- p |> transmute(Symbol = symbol,
                    `Moves with` = moves_with,
                    Value = value,
                    `Share of book` = weight,
                    `Gain or loss` = plpc,
                    `In dollars` = pl)
dark_dt(p, options = list(pageLength = 12, dom = "ftip")) |>
  formatCurrency("Value", digits = 0) |>
  formatCurrency("In dollars", digits = 0) |>
  formatPercentage("Share of book", 2) |>
  formatPercentage("Gain or loss", 1) |>
  formatStyle("Gain or loss", color = styleInterval(0, c(bad, good)), fontWeight = "bold")
```

# Trades

## Row {height="12%"}

```{r}
#| content: valuebox
#| title: "Orders sent, last 90 days"
o <- tbl(d$orders)
list(icon = "send", color = "light", value = nrow(o))
```

```{r}
#| content: valuebox
#| title: "Filled"
o <- tbl(d$orders)
list(icon = "check2-circle", color = "light",
     value = if (nrow(o)) sum(o$status == "filled") else 0)
```

```{r}
#| content: valuebox
#| title: "Finished trades"
rt <- tbl(d$roundtrips)
list(icon = "arrow-left-right", color = "light", value = nrow(rt))
```

```{r}
#| content: valuebox
#| title: "Money made on finished trades"
rt <- tbl(d$roundtrips)
list(icon = "cash-stack",
     color = if (!nrow(rt)) "secondary" else tone(sum(rt$pl)),
     value = if (!nrow(rt)) "none yet" else usd(sum(rt$pl)))
```

```{r}
#| content: valuebox
#| title: "Of those, how many won"
rt <- tbl(d$roundtrips)
list(icon = "trophy",
     color = "light",
     value = if (!nrow(rt)) "n/a"
             else paste0(sum(rt$pl > 0), " of ", nrow(rt)))
```

```{r}
#| content: valuebox
#| title: "Typical days held"
rt <- tbl(d$roundtrips)
list(icon = "hourglass-split", color = "light",
     value = if (!nrow(rt)) "n/a" else sprintf("%.1f", median(rt$held_days)))
```

## Row {height="30%"}

### Column {width="60%"}

```{r}
#| title: "When each stock was bought and when it was let go"
#| fig-width: 7.2
#| fig-height: 9
o <- tbl(d$orders)
if (nrow(o)) {
  f <- o |> filter(status == "filled", !is.na(filled_at)) |>
    mutate(t = as.POSIXct(substr(filled_at, 1, 19), format = "%Y-%m-%dT%H:%M:%S",
                          tz = "America/New_York"))
  span <- f |> group_by(symbol) |>
    summarise(first = min(t), last = max(t),
              open = !any(side == "sell"), .groups = "drop") |>
    arrange(first) |> mutate(symbol = factor(symbol, levels = symbol))
  f$symbol <- factor(f$symbol, levels = levels(span$symbol))
  now <- as.POSIXct(substr(m$generated_at, 1, 19), format = "%Y-%m-%dT%H:%M:%S",
                    tz = "America/New_York")
  ggplot() +
    geom_segment(data = span,
                 aes(y = symbol, yend = symbol, x = first,
                     xend = ifelse(open, now, last)),
                 colour = grid, linewidth = 1.6) +
    geom_point(data = f, aes(t, symbol, colour = side, size = notional), alpha = 0.95) +
    scale_colour_manual(values = c(buy = accent, sell = warn), name = NULL,
                        labels = c(buy = "bought", sell = "sold")) +
    scale_size_continuous(range = c(0.9, 3.4), guide = "none") +
    labs(x = NULL, y = NULL,
         subtitle = paste0("One line per stock, running from its first purchase to its\n",
                           "sale, or to now if we still hold it. Dot size is the size\n",
                           "of the order in dollars.")) +
    theme(legend.position = "top",
          axis.text.y = element_text(size = 6.4, colour = mute))
} else blank("no orders in the last 90 days")
```

### Column {width="40%"}

```{r}
#| title: "What each finished trade made, and how long it was held"
rt <- tbl(d$roundtrips)
if (nrow(rt)) {
  rt <- rt |> mutate(win = pl > 0)
  ggplot(rt, aes(held_days, plpc, colour = win, size = abs(pl))) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    geom_point(alpha = 0.9) +
    scale_colour_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_size_continuous(range = c(1.4, 6), guide = "none") +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = "days the stock was held", y = NULL,
         subtitle = paste0("Each dot is one closed trade. Above the line it made money.\n",
                           "Dot size is the size of the gain or loss in dollars.\n",
                           "The strategy sells on a weekly schedule, not on a target,\n",
                           "so the holding times cluster around seven days."))
} else blank("nothing has been bought and sold yet")
```

## Row {height="34%" .tabset}

```{r}
#| title: "Finished trades"
rt <- tbl(d$roundtrips)
if (nrow(rt)) {
  x <- rt |> arrange(desc(sold_at)) |>
    transmute(Symbol = symbol,
              Bought = when(bought_at, 16),
              Sold = when(sold_at, 16),
              `Days held` = held_days,
              `Bought at` = buy_price, `Sold at` = sell_price,
              `Gain or loss` = plpc, `In dollars` = pl)
  dark_dt(x, options = list(pageLength = 12, dom = "ftip")) |>
    formatCurrency(c("Bought at", "Sold at"), digits = 2) |>
    formatCurrency("In dollars", digits = 0) |>
    formatPercentage("Gain or loss", 2) |>
    formatStyle("Gain or loss", color = styleInterval(0, c(bad, good)), fontWeight = "bold")
} else htmltools::HTML("<p>Nothing has been bought and sold yet.</p>")
```

```{r}
#| title: "Every order, newest first"
o <- tbl(d$orders)
if (nrow(o)) {
  x <- o |> arrange(desc(coalesce(filled_at, submitted_at))) |>
    transmute(Symbol = symbol,
              Side = side, Status = status,
              Sent = when(submitted_at),
              Filled = when(filled_at),
              Shares = qty, Price = price, Dollars = notional,
              `Minutes after the bell` = from_open,
              `Seconds to fill` = latency_s)
  dark_dt(x, options = list(pageLength = 15, dom = "ftip")) |>
    formatCurrency(c("Price"), digits = 2) |>
    formatCurrency("Dollars", digits = 0) |>
    formatRound("Shares", 3) |>
    formatStyle("Side", color = styleEqual(c("buy", "sell"), c(accent, warn)),
                fontWeight = "bold") |>
    formatStyle("Status", color = styleEqual(c("filled", "canceled", "rejected"),
                                             c(good, mute, bad)))
} else htmltools::HTML("<p>No orders in the last ninety days.</p>")
```

```{r}
#| title: "Everything that happened, in order"
tl <- tbl(d$timeline)
if (nrow(tl)) {
  x <- tl |> arrange(desc(t)) |>
    transmute(When = when(t),
              What = label, Detail = detail, Kind = kind)
  dark_dt(x, options = list(pageLength = 20, dom = "ftip")) |>
    formatStyle("Kind", color = styleEqual(
      c("buy", "sell", "rebalance", "report", "tick"),
      c(accent, warn, "#bc8cff", mute, good)))
} else htmltools::HTML("<p>Nothing recorded yet.</p>")
```

## Row {height="24%"}

### Column {width="55%"}

```{r}
#| title: "Cost per trade, each rebalance, against what we assumed"
s <- tbl(d$slippage)
if (nrow(s)) {
  s <- s |> mutate(cycle = as.Date(cycle))
  ggplot(s, aes(cycle)) +
    annotate("rect", xmin = min(s$cycle) - 1, xmax = max(s$cycle) + 1,
             ymin = s$model_low[1], ymax = s$model_high[1], fill = good, alpha = 0.16) +
    geom_segment(aes(xend = cycle, y = 0, yend = mean_bp), colour = grid) +
    geom_point(aes(y = mean_bp, colour = mean_bp > model_high), size = 4) +
    geom_point(aes(y = median_bp), shape = 21, fill = card, colour = ink, size = 2.6) +
    geom_text(aes(y = mean_bp, label = sprintf("%.1f", mean_bp)), vjust = -1.2,
              size = 3, colour = ink) +
    scale_colour_manual(values = c(`TRUE` = bad, `FALSE` = good), guide = "none") +
    labs(x = NULL, y = "basis points per fill",
         subtitle = paste0("Filled dot is the average, hollow dot the typical trade.\n",
                           "Green band is the 5 to 10 basis points we assumed. ",
                           "One basis point\nis a hundredth of one percent."))
} else blank("no trades yet")
```

### Column {width="45%"}

```{r}
#| title: "What time of day the orders actually filled"
o <- tbl(d$orders)
f <- if (nrow(o)) o |> filter(status == "filled", !is.na(from_open)) else o
if (nrow(f)) {
  ggplot(f, aes(from_open, fill = side)) +
    annotate("rect", xmin = -Inf, xmax = 15, ymin = 0, ymax = Inf,
             fill = bad, alpha = 0.14) +
    geom_histogram(binwidth = 10, colour = card, linewidth = 0.2) +
    scale_fill_manual(values = c(buy = accent, sell = warn), name = NULL,
                      labels = c(buy = "bought", sell = "sold")) +
    labs(x = "minutes after the 9:30 opening bell", y = "orders",
         subtitle = paste0("The red strip is the first fifteen minutes, where the gap\n",
                           "between what buyers offer and sellers ask is widest and\n",
                           "trading costs most. Orders sent overnight all land there.")) +
    theme(legend.position = "top")
} else blank("no fills yet")
```

# Markets

## Row {height="34%"}

```{r}
#| title: "How the big markets and every sector have moved"
ms <- d$markets$series
if (length(ms)) {
  rows <- lapply(names(ms), function(k) {
    x <- ms[[k]]
    data.frame(Symbol = k, Name = x$name %||% k, Role = x$role,
               Last = x$last %||% NA_real_,
               Today = x$day %||% NA_real_, Week = x$w1 %||% NA_real_,
               Month = x$m1 %||% NA_real_, `Three months` = x$m3 %||% NA_real_,
               `Six months` = x$m6 %||% NA_real_, Year = x$y1 %||% NA_real_,
               RSI = x$rsi %||% NA_real_, MACD = x$macd_state,
               Held = x$held, check.names = FALSE, stringsAsFactors = FALSE)
  })
  tb <- bind_rows(rows) |>
    filter(Role %in% c("index", "sector")) |>
    arrange(desc(Month)) |>
    mutate(MACD = ifelse(MACD == "above", "rising", "falling"),
           Held = ifelse(Held, "yes", ""))
  cols <- c("Today", "Week", "Month", "Three months", "Six months", "Year")
  dark_dt(tb |> select(-Role),
          options = list(pageLength = 16, dom = "t", scrollX = TRUE)) |>
    formatCurrency("Last", digits = 2) |>
    formatPercentage(cols, 1) |>
    formatRound("RSI", 0) |>
    formatStyle(cols, color = styleInterval(0, c(bad, good))) |>
    formatStyle("MACD", color = styleEqual(c("rising", "falling"), c(good, bad)))
} else htmltools::HTML("<p>No market data.</p>")
```

::: {.card title="Reading this table"}
Each row is a fund that stands for one slice of the market: SPY is the whole US
market, QQQ the big technology names, IWM the small companies, GLD gold, TLT
long government bonds, and every XL- fund one industry. The percentage columns
are price change over that stretch, so **Month** means "up or down this much
since a month ago". **RSI** is a 0-100 speed gauge: above 70 the price has run
up fast and often pauses, below 30 it has fallen fast. **MACD** compares a fast
average of the price against a slow one; *rising* means the fast one is above,
which is the trend-following read that the book's own signal uses.
:::

## Row {height="52%" .tabset}

```{r}
#| output: asis
ms <- d$markets$series

# One drawing routine, called once per tab. Three stacked panels sharing an
# x axis: the candles with three trend averages, then MACD, then volume. The
# MACD is the same 12/26/9 the research chapters use, so a number here and a
# number in a notebook mean the same thing.
draw_symbol <- function(sym) {
  x <- ms[[sym]]
  b <- tbl(x$bars)
  if (!nrow(b)) return(blank(paste("no bars for", sym)))
  b <- b |> mutate(date = as.Date(date), up = close >= open)
  cndl <- ggplot(b, aes(date)) +
    geom_linerange(aes(ymin = low, ymax = high, colour = up), linewidth = 0.3) +
    geom_linerange(aes(ymin = pmin(open, close), ymax = pmax(open, close),
                       colour = up), linewidth = 1.5) +
    geom_line(aes(y = ema20), colour = accent, linewidth = 0.45, na.rm = TRUE) +
    geom_line(aes(y = ema50), colour = warn, linewidth = 0.45, na.rm = TRUE) +
    geom_line(aes(y = ema200), colour = "#bc8cff", linewidth = 0.5, na.rm = TRUE) +
    scale_colour_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         title = paste0(sym, if (!identical(x$name, sym)) paste0("   ", x$name) else "",
                        "    $", formatC(x$last, format = "f", digits = 2),
                        "    today ", pct(x$day %||% NA, 1),
                        ", month ", pct(x$m1 %||% NA, 1),
                        ", year ", pct(x$y1 %||% NA, 1)),
         subtitle = paste0("Each candle is one day: the thin line is the day's full range,\n",
                           "the thick body runs from the opening price to the close.\n",
                           "Green closed up, red closed down. The three curves are average\n",
                           "prices over the last 20 days (blue), 50 (amber) and 200 (violet).",
                           if ((x$clipped %||% 0) > 0)
                             paste0("\n", x$clipped, " day's range came back from the feed with a",
                                    " misplaced decimal\npoint and was pulled in to that day's",
                                    " opening and closing price.")
                           else "")) +
    theme(axis.text.x = element_blank())

  macd <- ggplot(b, aes(date)) +
    geom_col(aes(y = hist, fill = hist >= 0), width = 1, na.rm = TRUE) +
    geom_line(aes(y = macd), colour = accent, linewidth = 0.5, na.rm = TRUE) +
    geom_line(aes(y = signal), colour = warn, linewidth = 0.5, na.rm = TRUE) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    labs(x = NULL, y = "MACD",
         subtitle = paste0("Blue is a fast price average minus a slow one; amber is a smoothed\n",
                           "copy of blue. Bars are the gap between them. Bars crossing above\n",
                           "zero is the classic buy signal, below zero the classic sell.")) +
    theme(axis.text.x = element_blank())

  vol <- ggplot(b, aes(date, volume, fill = up)) +
    geom_col(width = 1) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_y_continuous(labels = label_number(scale_cut = cut_short_scale())) +
    labs(x = NULL, y = "shares traded",
         subtitle = "How many shares changed hands. A big move on thin volume is weaker.")

  cndl / macd / vol + plot_layout(heights = c(3, 1.5, 1))
}

# The symbols are not known until the data is read, so each tab is knitted as a
# child document. Printing chunk text would not work: by the time this runs,
# knitr has finished looking for chunks to execute.
picks <- unique(c(d$markets$watch, d$markets$focus))
picks <- picks[picks %in% names(ms)]
parts <- lapply(picks, function(s) {
  knitr::knit_child(
    text = c(sprintf("```{r}"),
             sprintf("#| title: \"%s\"", s),
             "#| fig-height: 7",
             "#| fig-width: 9.5",
             sprintf("draw_symbol(\"%s\")", s),
             "```"),
    envir = environment(), quiet = TRUE)
})
cat(unlist(parts), sep = "\n\n")
```

## Row {height="14%"}

::: {.card title="Which symbols appear here"}
The first five tabs are the markets the book measures itself against: **SPY**
the whole US market, **QQQ** the big technology names, **IWM** the small
companies, **GLD** gold and **TLT** long government bonds. The tabs after them
are the four holdings currently moving the account most, in either direction,
so they change as the book changes. Every sector fund is in the table above
even when it has no tab.
:::

# Analysis

```{r}
#| include: false
# The analysis blocks come from their own emitter, because they are built by
# the lab engines under outputs/1A-macd, 1B-confluence and 1C-fibonacci rather
# than by the dashboard's own arithmetic. A missing file blanks this page and
# leaves the rest of the dashboard alone.
a_path <- file.path(dirname(data_path), "analysis.json")
A <- if (file.exists(a_path)) fromJSON(a_path, simplifyVector = TRUE) else NULL
dv <- tbl(A$divergence); sc <- tbl(A$screen); sn <- A$screen_note
spy_row <- if (nrow(dv)) dv[dv$symbol == "SPY", , drop = FALSE] else dv
```

## Row {height="5%"}

```{r}
#| content: valuebox
#| title: "Names clearing all four gates"
list(icon = "funnel", color = "light",
     value = if (is.null(sn)) "n/a" else paste0(sn$passed, " of ", sn$n))
```

```{r}
#| content: valuebox
#| title: "Buy signals in the last 120 days"
list(icon = "arrow-up-circle", color = "success",
     value = if (!nrow(dv)) "n/a" else sum(dv$guarded_buy))
```

```{r}
#| content: valuebox
#| title: "Sell signals, same window"
list(icon = "arrow-down-circle", color = "danger",
     value = if (!nrow(dv)) "n/a" else sum(dv$guarded_sell))
```

```{r}
#| content: valuebox
#| title: "Names where price and momentum disagree"
list(icon = "shuffle", color = "warning",
     value = if (!nrow(dv)) "n/a" else sum(dv$bull > 0 | dv$bear > 0))
```

```{r}
#| content: valuebox
#| title: "The market's own momentum (SPY)"
list(icon = "activity",
     color = if (!nrow(spy_row)) "secondary"
             else if (spy_row$stance[1] == "above") "success" else "danger",
     value = if (!nrow(spy_row)) "n/a"
             else paste0("fast avg ", spy_row$stance[1]))
```

```{r}
#| content: valuebox
#| title: "Signal fired most recently"
list(icon = "broadcast", color = "light",
     value = if (!nrow(dv) || all(is.na(dv$signal_bars_ago))) "none"
             else paste0(dv$symbol[1], " ", dv$signal[1]))
```

## Row {height="5%"}

::: {.card title="What this page is, and what it is not"}
These are the engines from the workflow notebook, the guarded MACD, the
confluence score, the Fibonacci swing and the four-gate screen, run on **the
market we actually trade** rather than on the crypto pairs they were developed
against. The code is imported and called unchanged from `outputs/1A-macd`,
`outputs/1B-confluence`, `outputs/1C-fibonacci`, so a number here is computed
by the same lines the notebook documents. It reads
`r if (is.null(A)) "no data" else paste(A$meta$universe, "symbols")`:
the funds that stand for each slice of the market, and every stock the book
holds, over about two years of daily bars.

**None of this picks the book's trades.** The live strategy is 12-1 momentum
rebalanced weekly, and it does not consult MACD. This page is here to tell you
what the market is doing under the position you already hold, and to keep the
three months of work visible and running instead of frozen in a PNG. Judge a
signal here as information, not as an instruction.
:::

## Row {height="22%"}

### Column {width="52%"}

```{r}
#| title: "Divergence matrix: where price and momentum disagree, name by name"
#| fig-width: 7.5
#| fig-height: 8
if (nrow(dv)) {
  act <- dv |>
    mutate(activity = bull + bear + guarded_buy + guarded_sell) |>
    filter(activity > 0) |> arrange(desc(activity)) |> head(28)
  long <- act |>
    select(symbol, `Bullish divergence` = bull, `Bearish divergence` = bear,
           `Buy signal` = guarded_buy, `Sell signal` = guarded_sell) |>
    pivot_longer(-symbol, names_to = "kind", values_to = "n") |>
    mutate(symbol = factor(symbol, levels = rev(act$symbol)),
           kind = factor(kind, levels = c("Bullish divergence", "Bearish divergence",
                                          "Buy signal", "Sell signal")))
  ggplot(long, aes(kind, symbol, fill = n)) +
    geom_tile(colour = card, linewidth = 0.8) +
    geom_text(aes(label = ifelse(n > 0, n, "")), size = 2.9, colour = ink) +
    scale_fill_gradient(low = "#1b2230", high = accent, guide = "none") +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Counts over the last 120 trading days. A divergence is price\n",
                           "making a new high while the momentum behind it does not,\n",
                           "or the mirror of that at a low. It is the one reading that\n",
                           "is about the market changing its mind rather than\n",
                           "confirming what the price already did.")) +
    theme(axis.text.x = element_text(angle = 20, hjust = 1, size = 8),
          axis.text.y = element_text(size = 7.4),
          panel.grid = element_blank())
} else blank("no analysis data")
```

### Column {width="48%"}

```{r}
#| title: "What fired most recently, and how strongly"
#| fig-width: 7.5
#| fig-height: 8
if (nrow(dv) && any(!is.na(dv$signal_bars_ago))) {
  f <- dv |> filter(!is.na(signal_bars_ago)) |>
    arrange(signal_bars_ago) |> head(28) |>
    mutate(symbol = factor(symbol, levels = rev(symbol)))
  ggplot(f, aes(strength, symbol, colour = signal)) +
    geom_vline(xintercept = 0, colour = mute, linewidth = 0.3) +
    geom_segment(aes(x = 0, xend = strength, yend = symbol), linewidth = 0.7) +
    geom_point(size = 2.6) +
    geom_text(aes(label = paste0(signal_bars_ago, "d ago"),
                  hjust = ifelse(strength >= 0, -0.25, 1.25)),
              size = 2.6, colour = mute) +
    scale_colour_manual(values = c(buy = good, sell = bad), name = NULL) +
    scale_x_continuous(limits = c(-115, 115)) +
    labs(x = "conviction score, buy positive and sell negative", y = NULL,
         subtitle = paste0("Only crossings big enough to clear the engine's own noise\n",
                           "band and hold their direction count as a signal, which is\n",
                           "what 'guarded' means. The score blends how far it cleared\n",
                           "that band, how fast it is moving, and whether a divergence\n",
                           "agreed. Days ago is trading days.")) +
    theme(legend.position = "top", axis.text.y = element_text(size = 7.4))
} else blank("nothing has fired a guarded signal")
```

## Row {height="15%"}

### Column {width="55%"}

```{r}
#| title: "The four-gate screen, run on this market"
if (nrow(sc)) {
  s <- sc |> mutate(gate = ifelse(passed, "clears every gate", "blocked"))
  ggplot(s, aes(vol_m, atr, colour = gate)) +
    annotate("rect", xmin = sn$n * 0 + 20, xmax = Inf,
             ymin = A$meta$gates$atr_floor, ymax = A$meta$gates$atr_ceiling,
             fill = good, alpha = 0.10) +
    geom_hline(yintercept = c(A$meta$gates$atr_floor, A$meta$gates$atr_ceiling),
               linetype = "dashed", colour = warn, linewidth = 0.4) +
    geom_vline(xintercept = 20, linetype = "dashed", colour = accent, linewidth = 0.4) +
    geom_point(size = 2, alpha = 0.9) +
    scale_x_log10(labels = label_number(scale_cut = cut_short_scale())) +
    scale_colour_manual(values = c(`clears every gate` = good, blocked = bad),
                        name = NULL) +
    labs(x = "millions of dollars traded on a typical day (log scale)",
         y = "typical daily move, percent",
         subtitle = paste0("Shaded box is where a name is tradeable: busy enough to get\n",
                           "in and out of, moving enough to pay for the fee, not so wild\n",
                           "it cannot be sized. Dashed lines are the limits themselves.")) +
    theme(legend.position = "top")
} else blank("no screen data")
```

### Column {width="45%"}

::: {.card title="Which gate is actually doing the work"}
```{r}
#| output: asis
if (!is.null(sn)) {
  cat(sprintf(
"Of **%d names**, **%d clear all four gates**.

A gate that never blocks anything is not protecting you, so here is what each
one caught. Too little trading: **%d**. Outside the movement band of %.0f%% to
%.0f%% a day: **%d**. Gap between what buyers offer and sellers ask too wide:
**%d**. Not enough history to rank: **%d**.

One caveat that matters. Daily bars carry no record of the actual gap between
bid and ask, so it is estimated from how much consecutive daily ranges overlap.
For **%d of the %d** names that estimate comes back as exactly zero, which means
*too tight for this method to resolve*, not *free*. The gate still blocks %d
names, so it is doing real work, but treat a zero as unmeasured.\n\n",
    sn$n, sn$passed, sn$blocked_by_liquidity,
    A$meta$gates$atr_floor, A$meta$gates$atr_ceiling, sn$blocked_by_atr,
    sn$blocked_by_spread, sn$blocked_by_history,
    sn$spread_unresolved, sn$n, sn$blocked_by_spread))
} else cat("No screen data.\n")
```
:::

## Row {height="32%" .tabset}

```{r}
#| output: asis
# The three lab dashboards keep their symbol dropdown, which is the whole point
# of them, so they are shown as the live pages they are rather than flattened
# to a picture. They sit beside dashboard.html in dashboard/analysis/.
pg <- tbl(A$pages)
if (nrow(pg)) {
  parts <- lapply(seq_len(nrow(pg)), function(i) {
    r <- pg[i, ]
    knitr::knit_child(text = c(
      sprintf("```{r}"),
      sprintf("#| title: \"%s\"", r$title),
      # The address is NOT written into the frame. Pandoc's self-contained pass
      # resolves src, href and data-src alike, and with any of them it pulled
      # all three analysis pages in whole and took the dashboard from 10 MB to
      # 40. It leaves data-page alone, and the script below turns that key into
      # an address in the browser, where nothing is inlined.
      sprintf("htmltools::tagList(htmltools::tags$p(\"%s\", style=\"color:#8b98a9;font-size:.82rem;margin:.2rem 0 .4rem\"), htmltools::tags$iframe(class=\"analysis-frame\", `data-page`=\"%s\", style=\"width:100%%;height:560px;border:0;background:#161b22\"))",
              gsub('"', "'", r$blurb), r$key),
      "```"), envir = environment(), quiet = TRUE)
  })
  cat(unlist(parts), sep = "\n\n")
} else {
  cat("::: {.card}\nThe interactive dashboards were not built. Run ",
      "`.venv/bin/python inputs/analysis_charts.py`.\n:::\n")
}
```

## Row {height="4%"}

::: {.card title="Opening the interactive dashboards on their own"}
The three tabs above are live pages, not pictures: each carries a dropdown that
switches between all `r if (is.null(A)) "the" else A$meta$universe` symbols, and
every chart zooms and reads out a value on hover. They are written as separate
files so the main page stays quick to open, and they sit in
`dashboard/analysis/`. Open them directly at
`dashboard/analysis/macd.html`, `confluence.html` and `fibonacci.html`.
Because they are separate files, `dashboard.html` must travel with the
`analysis/` folder beside it for the frames above to fill.

```{=html}
<script>
// The frames above carry their address in data-src rather than src, because the
// page is built as one self-contained file and pandoc inlines anything it can
// resolve: with a plain src the three analysis pages were pulled in whole and
// the dashboard went from 10 MB to 35 MB. This fills the address in once the
// frame is actually on screen, so nothing is fetched until you open its tab.
(function () {
  var PAGES = {
    macd: "analysis/macd.html",
    confluence: "analysis/confluence.html",
    fibonacci: "analysis/fibonacci.html"
  };
  function arm() {
    document.querySelectorAll('iframe.analysis-frame').forEach(function (f) {
      var key = f.getAttribute('data-page');
      if (!f.getAttribute('src') && f.offsetParent !== null && PAGES[key]) {
        f.setAttribute('src', PAGES[key]);
      }
    });
  }
  document.addEventListener('DOMContentLoaded', arm);
  document.addEventListener('click', function () { setTimeout(arm, 80); });
  window.addEventListener('load', arm);
})();
</script>
```
:::

## Row {height="17%" .tabset}

```{r}
#| output: asis
# One study sheet per symbol: candles, the MACD underneath, and a marker at
# every place a guarded signal or a divergence actually fired. This is the
# sheet the workflow used to grade a signal after the fact.
draw_journal <- function(sym) {
  j <- A$journal[[sym]]
  b <- tbl(j$bars)
  if (!nrow(b)) return(blank(paste("no bars for", sym)))
  b <- b |> mutate(date = as.Date(date), up = close >= open)
  fired <- b |> filter(buy | sell) |>
    mutate(what = ifelse(buy, "buy", "sell"),
           y = ifelse(buy, low * 0.985, high * 1.015))
  divs <- b |> filter(bull | bear) |>
    mutate(what = ifelse(bull, "price and momentum disagree, upward",
                         "price and momentum disagree, downward"),
           y = ifelse(bull, low * 0.97, high * 1.03))

  px <- ggplot(b, aes(date)) +
    geom_linerange(aes(ymin = low, ymax = high, colour = up), linewidth = 0.3) +
    geom_linerange(aes(ymin = pmin(open, close), ymax = pmax(open, close),
                       colour = up), linewidth = 1.4) +
    geom_line(aes(y = ema20), colour = accent, linewidth = 0.4, na.rm = TRUE) +
    geom_line(aes(y = ema50), colour = warn, linewidth = 0.4, na.rm = TRUE) +
    scale_colour_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL, title = sym,
         subtitle = paste0("Triangles are guarded signals: crossings big enough to clear\n",
                           "the engine's noise band. Circles are divergences.")) +
    theme(axis.text.x = element_blank())
  if (nrow(fired))
    px <- px + geom_point(data = fired, aes(y = y, shape = what, fill = what),
                          size = 2.4, colour = ink, stroke = 0.3) +
      scale_shape_manual(values = c(buy = 24, sell = 25), name = NULL) +
      scale_fill_manual(values = c(buy = good, sell = bad), name = NULL)
  if (nrow(divs))
    px <- px + geom_point(data = divs, aes(y = y), shape = 21, size = 2,
                          fill = warn, colour = ink, stroke = 0.3)
  # the Fibonacci levels this swing is working inside
  fb <- j$fib
  if (length(fb)) {
    gp <- c(fb[["golden_low"]], fb[["golden_high"]])
    if (length(gp) == 2 && all(is.finite(gp)))
      px <- px + annotate("rect", xmin = min(b$date), xmax = max(b$date),
                          ymin = gp[1], ymax = gp[2], fill = "#bc8cff", alpha = 0.10)
    for (k in c("0.382", "0.5", "0.618"))
      if (!is.null(fb[[k]]))
        px <- px + annotate("segment", x = min(b$date), xend = max(b$date),
                            y = fb[[k]], yend = fb[[k]],
                            colour = "#bc8cff", linewidth = 0.3, linetype = "dotted")
  }

  md <- ggplot(b, aes(date)) +
    geom_col(aes(y = hist, fill = hist >= 0), width = 1, na.rm = TRUE) +
    geom_line(aes(y = macd), colour = accent, linewidth = 0.45, na.rm = TRUE) +
    geom_line(aes(y = signal), colour = warn, linewidth = 0.45, na.rm = TRUE) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    labs(x = NULL, y = "MACD", subtitle = NULL) +
    theme(axis.text.x = element_blank())

  cf <- ggplot(b, aes(date, score)) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    geom_col(aes(fill = score >= 0), width = 1, na.rm = TRUE) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    labs(x = NULL, y = "agreement",
         subtitle = paste0("Four readings scored together: the MACD stance, which side of its\n",
                           "averages the price sits, the candle shape, and where it is inside\n",
                           "the Fibonacci swing. Positive means they agree upward."))

  px / md / cf + plot_layout(heights = c(3, 1.3, 1.3))
}

syms <- if (is.null(A)) character(0) else intersect(A$journal_for, names(A$journal))
if (length(syms)) {
  parts <- lapply(syms, function(s) {
    knitr::knit_child(text = c("```{r}",
                               sprintf("#| title: \"%s\"", s),
                               "#| fig-height: 7",
                               "#| fig-width: 10",
                               sprintf("draw_journal(\"%s\")", s),
                               "```"), envir = environment(), quiet = TRUE)
  })
  cat(unlist(parts), sep = "\n\n")
} else cat("::: {.card}\nNo study sheets were built.\n:::\n")
```

# Rules

## Row {height="32%"}

```{r}
#| title: "Every safety rule, and whether it is holding right now"
g <- tbl(d$guards) |> transmute(Rule = name, `In plain words` = plain,
                               Status = state, `Right now` = value, Detail = detail)
dark_dt(g, options = list(dom = "t", pageLength = 20)) |>
  formatStyle("Status", fontWeight = "bold",
              color = styleEqual(c("OK", "DRIFT", "BREACH", "TRIPPED", "FIRING", "STOPPED"),
                                 c(good, warn, bad, bad, bad, bad)))
```

## Row {height="40%"}

### Column {width="55%"}

```{r}
#| title: "How often it actually rebalanced, against the seven days it intends"
cy <- d$cycles
ds <- as.Date(unlist(cy$dates))
if (length(ds) > 1) {
  gp <- data.frame(when = ds[-1], gap = as.numeric(diff(ds)))
  ggplot(gp, aes(when, gap)) +
    geom_hline(yintercept = 7, linetype = "dashed", colour = accent) +
    geom_col(aes(fill = gap > 7), width = 0.5) +
    geom_text(aes(label = paste0(gap, "d")), vjust = -0.6, size = 3, colour = ink) +
    scale_fill_manual(values = c(`TRUE` = warn, `FALSE` = good), guide = "none") +
    scale_y_continuous(expand = expansion(mult = c(0, 0.18))) +
    labs(x = NULL, y = "days since the one before",
         subtitle = paste0("Dashed line is the weekly cadence the evidence tested.\n",
                           "A bar above it is a cycle that ran late, which stretches\n",
                           "how long the trial takes to finish."))
} else blank("needs two rebalances before a gap exists")
```

### Column {width="45%"}

::: {.card title="How far through the test we are"}
```{r}
#| output: asis
cy <- d$cycles
cat(sprintf(
"This is a paper trial with one job: find out whether real trading costs match
what the strategy assumed. That takes about **%d clean weekly rebalances**, and
**%d** are done.

", cy$needed, cy$done))
n_late <- length(unlist(cy$late))
if (n_late > 0) {
  cat(sprintf("%d ran late. The longest gap between two was **%d days** against the
7 days the weekly cadence intends.\n\n", n_late, cy$worst_gap))
} else if (cy$done > 1) {
  cat("None have run late.\n\n")
} else {
  cat("Too few rebalances yet to say whether the cadence holds.\n\n")
}
cat("Until the trial finishes, nothing here says the strategy works with real
money. It says the plumbing does.\n")
```
:::

## Row {height="28%"}

::: {.card title="What the concentration bar means"}
```{r}
#| output: asis
cc <- d$concentration
if (isTRUE(cc$available)) {
  cat(sprintf(
"The biggest group of stocks that move together is **%d of the %d holdings**, worth
**%s of the money**. Your rules cap any such group at %s.

Momentum concentrates on purpose: last year's winners are last year's winning
industry. That is why the book can lose six percent in a week the market barely
moves, and win it back the next day. Both are the same fact.

Right now **%d holding%s sit%s over the cap**, worst is %s at %s.\n\n",
    cc$biggest_group_names, h$positions, percent(cc$biggest_group_weight, 0.1),
    percent(cc$cap, 1), cc$over_cap, ifelse(cc$over_cap == 1, "", "s"),
    ifelse(cc$over_cap == 1, "s", ""), cc$worst_local_symbol,
    percent(cc$worst_local_weight, 0.1)))
}
```
:::

# History

## Row {height="40%"}

### Column {width="60%"}

```{r}
#| title: "What every past run of this page reported"
ar <- tbl(d$archive)
if (nrow(ar) > 1) {
  ar <- ar |> mutate(t = as.POSIXct(substr(generated_at, 1, 19),
                                    format = "%Y-%m-%dT%H:%M:%S",
                                    tz = "America/New_York"))
  ggplot(ar, aes(t, equity)) +
    geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
    geom_line(colour = accent, linewidth = 0.7) +
    geom_point(colour = accent, size = 1.4) +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Each dot is one refresh of this dashboard, stamped when it\n",
                           "ran. It is the page's memory of itself: if a figure here ever\n",
                           "disagrees with what an earlier run said, this is where that\n",
                           "shows up."))
} else blank("this is the first run kept in the archive")
```

### Column {width="40%"}

```{r}
#| title: "What each written report claimed at the time"
rp <- tbl(d$reports)
if (nrow(rp) > 1) {
  rp <- rp |> filter(!is.na(equity)) |>
    mutate(t = as.POSIXct(paste(date, time), format = "%Y-%m-%d %H:%M",
                          tz = "America/New_York"))
  ggplot(rp, aes(t, equity)) +
    geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
    geom_step(colour = warn, linewidth = 0.7) +
    geom_point(colour = warn, size = 2) +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("The account value stated in each daily markdown report\n",
                           "under outputs/AA-evals/. Two lines that should agree:\n",
                           "this one and the one to its left."))
} else blank("fewer than two reports written so far")
```

## Row {height="30%"}

```{r}
#| title: "The written reports, newest first"
rp <- tbl(d$reports)
if (nrow(rp)) {
  x <- rp |> arrange(desc(date), desc(time)) |>
    transmute(Date = date, Time = time,
              `Account value it reported` = equity,
              `Change since live it reported` = since_live,
              File = file, KB = kb)
  dark_dt(x, options = list(pageLength = 12, dom = "ftip")) |>
    formatCurrency("Account value it reported", digits = 0) |>
    formatPercentage("Change since live it reported", 2) |>
    formatStyle("Change since live it reported",
                color = styleInterval(0, c(bad, good)))
} else htmltools::HTML("<p>No reports written yet.</p>")
```

## Row {height="30%"}

```{r}
#| title: "Every refresh of this page that was kept"
ar <- tbl(d$archive)
if (nrow(ar)) {
  x <- ar |> arrange(desc(generated_at)) |>
    transmute(When = when(generated_at),
              `Account value` = equity,
              `Since live` = since_live,
              Holdings = positions,
              `Cash share` = cash_pct,
              `Below its peak` = from_peak,
              `Cycles done` = cycles_done,
              `Rules not OK` = vapply(guards_bad, function(v)
                if (length(v)) paste(v, collapse = ", ") else "none", character(1)),
              File = file)
  dark_dt(x, options = list(pageLength = 12, dom = "ftip")) |>
    formatCurrency("Account value", digits = 0) |>
    formatPercentage(c("Since live", "Cash share", "Below its peak"), 2) |>
    formatStyle("Since live", color = styleInterval(0, c(bad, good))) |>
    formatStyle("Rules not OK", color = styleEqual("none", good))
} else htmltools::HTML("<p>Nothing archived yet.</p>")
```

# Research

```{r}
#| include: false
f_path <- file.path(dirname(data_path), "figures.json")
FG <- if (file.exists(f_path)) fromJSON(f_path, simplifyVector = TRUE) else NULL
figs <- tbl(FG$figures)
# Relative to this file, not absolute: an absolute path inside a markdown image
# is read as root-relative, and pandoc then hunts for ./Volumes/... and gives up.
figroot <- ".."
```

## Row {height="4%"}

::: {.card title="Three months of analysis, and where it stands"}
Every figure below was produced during the research that built this system, and
each one is shown here with the caption the README gives it. They are the
record of the work, not a live view: almost all of them are drawn on **Binance
crypto bars**, on an hourly or four-hour frame, for a strategy that the
out-of-sample tests eventually killed. The live book is US equities on a weekly
momentum rule.

That is exactly why they matter and why they are kept. The reason the book
trades equities at all is that these figures, and the tests behind them, failed
to find an edge in crypto that survived fees. The **Analysis** page runs the
same engines on today's market; this page is where they came from.
`r nrow(figs)` figures, grouped by the chapter they belong to.
:::

```{r}
#| output: asis
# One card per figure, two to a row, grouped under the chapter heading the
# README gives it. No row height is set: this page is a scrolling contact
# sheet, and a percentage here would fight the number of figures. The image is
# a smaller copy so the page stays quick, and the caption and section are the
# README's own words rather than new ones written here.
if (nrow(figs)) {
  figs$section[figs$section == ""] <- "Overview"
  # Row heights on a page must sum to 100 or the first row swallows the screen.
  # This page's row count is not known until the figures are counted, so the
  # share is worked out here rather than typed in.
  n_rows <- ceiling(nrow(figs) / 2)
  each <- (100 - 4 - 10) / n_rows
  for (secn in unique(figs$section)) {
    part <- figs[figs$section == secn, , drop = FALSE]
    for (i in seq_len(nrow(part))) {
      if (i %% 2 == 1) cat(sprintf("\n\n## Row {height=\"%.1f%%\"}\n\n", each))
      r <- part[i, ]
      cat(sprintf("::: {.card title=\"%s\"}\n", gsub('"', "'", r$caption)))
      cat(sprintf("**%s%s**\n\n", secn,
                  if (nzchar(r$sub)) paste0(" — ", r$sub) else ""))
      cat(sprintf("![](%s)\n\n", file.path(figroot, r$thumb)))
      if (nzchar(r$blurb)) cat(gsub("^\\*|\\*$", "", r$blurb), "\n\n")
      cat(sprintf("<span style=\"color:#8b98a9;font-size:.78rem\">Full size in the repo at `%s`</span>\n",
                  r$path))
      cat(":::\n\n")
    }
  }
} else {
  cat("\n\n## Row\n\n::: {.card}\nNo figure index. Run ",
      "`.venv/bin/python inputs/research_figures.py`.\n:::\n")
}
```

## Row {height="10%"}

::: {.card title="Figures the notebook draws but does not save"}
```{r}
#| output: asis
nbf <- tbl(FG$notebook)
if (nrow(nbf)) {
  cat(sprintf("The workflow notebook renders %d more drawings inside the document rather than saving them, so they are not shown above. Running the notebook regenerates each one. They are:\n\n", nrow(nbf)))
  for (i in seq_len(nrow(nbf)))
    cat(sprintf("- **%s** — %s\n", nbf$section[i], nbf$what[i]))
  cat("\n")
} else cat("None recorded.\n")
```
:::
