---
title: "Swing trader"
format:
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
    theme: [darkly, dashboard.scss]
    nav-buttons:
      - icon: github
        href: https://github.com/seamusrobertmurphy/swing-trader
execute:
  echo: false
  warning: false
  message: false
# Nine candlestick panels at knitr's default resolution pushed the standalone
# page past ten megabytes, which is slow to open over a phone connection for no
# gain: nothing here is read at print resolution.
knitr:
  opts_chunk:
    dev: png
    dpi: 96
---

```{r setup}
library(jsonlite); library(ggplot2); library(dplyr); library(tidyr)
library(scales); library(DT); library(patchwork)

# Find the repo root by walking up until inputs/ appears, so this renders the
# same from the repo root, from dashboard/, or from anywhere a scheduler puts
# its working directory. DAYTRADER_DATA overrides it outright.
find_repo <- function(start = getwd()) {
  p <- normalizePath(start, mustWork = FALSE)
  for (i in 1:6) {
    if (dir.exists(file.path(p, "inputs"))) return(p)
    parent <- dirname(p); if (parent == p) break; p <- parent
  }
  stop("cannot locate the repo root from ", start)
}
data_path <- Sys.getenv("DAYTRADER_DATA",
                        file.path(find_repo(), "outputs", "dashboard", "data.json"))
if (!file.exists(data_path))
  stop("no data at ", data_path, " -- run: .venv/bin/python inputs/dashboard_data.py")
d <- fromJSON(data_path, simplifyVector = TRUE)
if (!length(d$headline)) stop("data.json has no headline block; the emitter failed")

h <- d$headline; m <- d$meta

# ---- palette -------------------------------------------------------------
# The same eight colours the stylesheet uses. Defined once here so a red in a
# chart is the same red as a red in a table.
bg   <- "#0d1117"; card <- "#161b22"
ink  <- "#e6edf3"; mute <- "#8b98a9"; grid <- "#242c36"
good <- "#2ea86b"; bad  <- "#e5534b"; warn <- "#d29922"; accent <- "#58a6ff"
neut <- "#6e7b8b"
# A categorical set that stays distinguishable on a dark ground and does not
# rely on red-green separation, which is the pair a colour-blind reader loses.
cats <- c("#58a6ff", "#2ea86b", "#d29922", "#bc8cff", "#39c5cf", "#e5534b",
          "#f78166", "#8ddb8c", "#a5a5f5", "#c9a227", "#7ee787", "#ff9bce",
          "#6e7b8b")

# An ISO stamp puts a T where a space belongs, which in a table reads as a typo.
when <- function(x, n = 19) sub("T", " ", substr(x, 1, n))

pct  <- function(x, dp = 2) ifelse(is.na(x), "n/a", sprintf(paste0("%+.", dp, "f%%"), 100 * x))
# formatC puts the minus inside the dollars ("$-1,484"), which reads as a
# typo rather than a loss.
usd  <- function(x) paste0(ifelse(x < 0, "-$", "$"),
                           formatC(abs(x), format = "f", big.mark = ",", digits = 0))
tone <- function(x) if (is.null(x) || is.na(x)) "secondary" else if (x >= 0) "success" else "danger"

# jsonlite hands back NULL for an absent block and a list for an empty array.
# Every panel below asks through this, so one missing feed blanks one card
# instead of failing the whole page.
`%||%` <- function(a, b) if (is.null(a) || length(a) == 0) b else a

tbl <- function(x) {
  if (is.null(x) || length(x) == 0) return(data.frame())
  if (is.data.frame(x)) return(x)
  as.data.frame(x, stringsAsFactors = FALSE)
}
blank <- function(msg) {
  ggplot() + annotate("text", 0, 0, label = msg, colour = mute, size = 4) +
    theme_void() + theme(plot.background = element_rect(fill = card, colour = NA))
}

theme_dark_book <- theme_minimal(base_size = 11) +
  theme(
    plot.background  = element_rect(fill = card, colour = NA),
    panel.background = element_rect(fill = card, colour = NA),
    legend.background = element_rect(fill = card, colour = NA),
    legend.key = element_rect(fill = card, colour = NA),
    panel.grid.major = element_line(colour = grid, linewidth = 0.3),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    text = element_text(colour = ink),
    axis.text = element_text(colour = mute, size = 8.5),
    axis.title = element_text(colour = mute, size = 8.5),
    legend.text = element_text(colour = mute, size = 8.5),
    strip.text = element_text(colour = ink, face = "bold", size = 9),
    plot.title.position = "plot",
    plot.title = element_text(face = "bold", size = 11, colour = ink),
    plot.subtitle = element_text(colour = mute, size = 8.8, lineheight = 1.15))
theme_set(theme_dark_book)

# A pie forces a square panel, so the drawing does not fill the width it was
# given and the leftover strip shows the drawing device's own background. That
# background is white by default, which on a dark page reads as two blank
# columns beside every pie. Set it once, for every chart on the page.
knitr::opts_chunk$set(dev.args = list(bg = card))

dark_dt <- function(x, ...) {
  datatable(x, rownames = FALSE, class = "compact stripe hover", ...)
}
```

# Money

## Row {height="15%"}

```{r}
#| content: valuebox
#| title: "Account value"
list(icon = "wallet2", color = tone(h$since_live), value = usd(h$equity))
```

```{r}
#| content: valuebox
#| title: "Since it went live"
list(icon = if (h$since_live >= 0) "graph-up" else "graph-down",
     color = tone(h$since_live), value = pct(h$since_live))
```

```{r}
#| content: valuebox
#| title: "The market, same days"
list(icon = "bank", color = "light",
     value = if (is.null(h$spy_since_live)) "n/a" else pct(h$spy_since_live))
```

```{r}
#| content: valuebox
#| title: "Ahead of or behind the market"
list(icon = "flag", color = tone(h$excess),
     value = if (is.null(h$excess)) "n/a" else pct(h$excess))
```

```{r}
#| content: valuebox
#| title: "Down from its best day"
list(icon = "arrow-down-right",
     color = if (h$from_peak > -0.05) "light" else "warning",
     value = pct(h$from_peak))
```

```{r}
#| content: valuebox
#| title: "Cost per trade vs the 5-10 assumed"
sl <- tbl(d$slippage)
list(icon = "cash-coin",
     color = if (!nrow(sl)) "secondary"
             else if (tail(sl$mean_bp, 1) <= 10) "success" else "danger",
     value = if (!nrow(sl)) "no trades"
             else paste0(sprintf("%.1f", tail(sl$mean_bp, 1)), " bp"))
```

```{r}
#| content: valuebox
#| title: "Clean cycles done"
list(icon = "arrow-repeat",
     color = if (d$cycles$done >= d$cycles$needed) "success" else "warning",
     value = paste0(d$cycles$done, " of ", d$cycles$needed))
```

## Row {height="10%"}

::: {.card title="What this page is"}
**This is fake money.** It is a paper account and the switch that would let it
spend real money is off.

`r m$mark_note` Marked `r m$generated_at_pretty`.
The book has been running `r m$sessions` trading sessions and holds
`r h$positions` stocks with `r sprintf("%.1f%%", 100*h$cash_pct)` in cash.
Was this move within expectations? **`r if (h$within_expectations) "Yes" else "No"`** —
the plan expected swings of about `r sprintf("%.1f%%", 100*h$expected_swing)` over
that stretch, and this is `r sprintf("%.1f", abs(h$sigmas))` times that.
:::

## Row {height="38%"}

### Column {width="62%"}

```{r}
#| title: "The book against the market, both starting at $100,000"
live <- as.Date(d$meta$live_from)
eq <- tbl(d$equity_curve) |> mutate(date = as.Date(date)) |>
      filter(date >= live) |> mutate(who = "The book")
bm <- if (length(d$benchmark$series)) {
  tbl(d$benchmark$series) |> mutate(date = as.Date(date),
      who = paste0("The market (", d$benchmark$symbol, ")"))
} else eq[0, ]
both <- bind_rows(eq, bm)

ggplot(both, aes(date, equity, colour = who)) +
  geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
  geom_line(linewidth = 0.9) +
  geom_point(data = filter(both, date == max(date)), size = 2.2) +
  scale_colour_manual(values = setNames(c(accent, neut), unique(both$who))) +
  scale_y_continuous(labels = dollar_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, colour = NULL,
       subtitle = "Dotted line is the starting stake. Above it is a profit.") +
  theme(legend.position = "top")
```

### Column {width="38%"}

```{r}
#| title: "How far below its best the account has been"
dd <- tbl(d$risk$drawdown)
if (nrow(dd)) {
  dd <- dd |> mutate(date = as.Date(date)) |> filter(date >= live)
  ggplot(dd, aes(date, dd)) +
    geom_area(fill = bad, alpha = 0.28) +
    geom_line(colour = bad, linewidth = 0.7) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Zero means it is at a new high. The deepest hole so far\n",
                           "was ", percent(d$risk$worst_dd, 0.1),
                           ". A 25% fall on any one stock sells it automatically.")) 
} else blank("not enough history yet")
```

## Row {height="37%"}

### Column {width="34%"}

```{r}
#| title: "What each day did"
dl <- tbl(d$risk$daily)
if (nrow(dl)) {
  dl <- dl |> mutate(date = as.Date(date)) |> filter(date >= live)
  ggplot(dl, aes(date, ret, fill = ret >= 0)) +
    geom_col(width = 0.6) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("One bar per trading day. ", d$risk$up_days, " up, ",
                           d$risk$down_days, " down. Best ",
                           percent(d$risk$best_day, 0.1), ", worst ",
                           percent(d$risk$worst_day, 0.1), "."))
} else blank("no full days yet")
```

### Column {width="34%"}

```{r}
#| title: "Today and the last few sessions, minute by minute"
it <- tbl(d$intraday)
if (nrow(it) > 2) {
  it <- it |> mutate(t = as.POSIXct(t, format = "%Y-%m-%dT%H:%M:%S", tz = "America/New_York"))
  ggplot(it, aes(t, equity)) +
    geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
    geom_line(colour = accent, linewidth = 0.6) +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Marked every 15 minutes while the market is open.\n",
                           "The flat stretches are nights and weekends, removed."))
} else blank("no intraday marks")
```

### Column {width="32%"}

```{r}
#| title: "How rough the ride is"
rv <- tbl(d$risk$rolling_vol)
if (nrow(rv) > 2) {
  rv <- rv |> mutate(date = as.Date(date))
  ggplot(rv, aes(date, vol)) +
    geom_hline(yintercept = 0.35, linetype = "dashed", colour = warn) +
    geom_line(colour = accent, linewidth = 0.8) +
    scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, NA)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("How much the account swings, stated as a year's worth.\n",
                           "Dashed line is the 35% the plan expected. Higher is rougher."))
} else blank("needs ten sessions before this means anything")
```

# What we own

## Row {height="30%"}

```{r}
#| title: "By what it moves with"
#| fig-width: 4.2
#| fig-height: 5.4
# One drawing routine for all four pies. A slice's share is written into its
# own legend entry rather than onto the slice, because at four pies to a row
# the thin slices have no room for a label and the reader ends up guessing.
donut <- function(df, palette = cats, order_by = "weight") {
  if (!nrow(df)) return(blank("nothing to show"))
  if (order_by == "weight") df <- df |> arrange(desc(weight))
  df <- df |> mutate(key = paste0(label, "   ", percent(weight, 0.1)),
                     key = factor(key, levels = key))
  ggplot(df, aes(x = 2, y = weight, fill = key)) +
    geom_col(width = 1, colour = card, linewidth = 0.5) +
    coord_polar(theta = "y") +
    xlim(0.4, 2.5) +
    scale_fill_manual(values = setNames(palette[seq_len(nrow(df))], levels(df$key)),
                      name = NULL) +
    theme_void(base_size = 9) +
    theme(plot.background = element_rect(fill = card, colour = NA),
          legend.background = element_rect(fill = card, colour = NA),
          legend.key.size = unit(11, "pt"),
          legend.text = element_text(colour = ink, size = 8.6),
          legend.position = "bottom",
          legend.direction = "vertical",
          legend.justification = "left",
          plot.margin = margin(2, 2, 2, 2))
}
donut(tbl(d$mix$sector))
```

```{r}
#| title: "By groups that move together"
#| fig-width: 4.2
#| fig-height: 5.4
donut(tbl(d$mix$cluster))
```

```{r}
#| title: "By how each holding is doing"
#| fig-width: 4.2
#| fig-height: 5.4
mv <- tbl(d$mix$move)
ord <- c("Down more than 10%", "Down 2 to 10%", "Roughly flat",
         "Up 2 to 10%", "Up more than 10%")
if (nrow(mv)) {
  mv <- mv |> mutate(label = factor(label, levels = ord)) |> arrange(label)
  donut(mv, palette = c(bad, "#b4514c", neut, "#3f9a67", good)[
    match(as.character(mv$label), ord)], order_by = "given")
} else blank("no holdings")
```

```{r}
#| title: "Where the shares are listed"
#| fig-width: 4.2
#| fig-height: 5.4
donut(tbl(d$mix$venue))
```

## Row {height="12%"}

::: {.card title="What the four pies are cutting"}
Same money, four ways of slicing it, because any one slice flatters and the
disagreement between them is the point. **What it moves with** files each
holding under the sector fund whose daily moves it has most closely followed
over the past year; there is no sector list in this repo, so this is a
measurement, not a label. **Groups that move together** is stricter: it joins
any two holdings whose daily moves agree more than `r percent(d$concentration$rho, 1)`
of the time, and your rules cap one such group at `r percent(d$concentration$cap, 1)`.
**How each holding is doing** measures against what we paid, a number used
nowhere else except the automatic 25% sell. **Where the shares are listed** is
the exchange, worth a glance because a thin exchange is a slower and dearer exit.
:::

## Row {height="30%"}

### Column {width="55%"}

```{r}
#| title: "Which holdings moved the whole account, in percentage points"
at <- tbl(d$attribution)
if (nrow(at)) {
  top <- bind_rows(head(at, 8), tail(at, 8)) |> distinct(symbol, .keep_all = TRUE) |>
    arrange(points) |> mutate(symbol = factor(symbol, levels = symbol))
  ggplot(top, aes(symbol, points, fill = points >= 0)) +
    geom_col(width = 0.7) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    geom_text(aes(label = sprintf("%+.2f", points),
                  hjust = ifelse(points >= 0, -0.15, 1.15)), size = 2.9, colour = ink) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    coord_flip(clip = "off") +
    scale_y_continuous(expand = expansion(mult = c(0.14, 0.14))) +
    labs(x = NULL, y = "percentage points of the whole account",
         subtitle = paste0("A stock down 20% at a 1.5% weight costs the book 0.3 points.\n",
                           "This ranks by the damage done, not by the stock's own fall."))
} else blank("no holdings")
```

### Column {width="45%"}

```{r}
#| title: "Is it one bet or fifty?"
cc <- d$concentration
if (isTRUE(cc$available)) {
  g   <- tbl(cc$groups)
  big <- g[g$n > 1, , drop = FALSE]
  ones<- g[g$n == 1, , drop = FALSE]
  rows <- data.frame(
    key    = as.character(big$rank),
    label  = paste0(big$n, " stocks that move together"),
    weight = big$weight, ord = big$weight, lone = FALSE, stringsAsFactors = FALSE)
  if (nrow(ones) > 0) {
    rows <- rbind(rows, data.frame(
      key    = "loners",
      label  = paste0(nrow(ones), " stocks on their own"),
      weight = sum(ones$weight), ord = -1, lone = TRUE, stringsAsFactors = FALSE))
  }
  # Two groups of the same size carry the same words, and the words were the
  # axis identity, so factor() hit a duplicated level and the whole page failed
  # to render (2026-08-27: three groups of two after the cluster-cap rebalance).
  # The group rank is the identity now; the words are only the printed label.
  rows$key <- factor(rows$key, levels = rows$key[order(rows$ord)])

  ggplot(rows, aes(key, weight)) +
    geom_col(aes(fill = !lone & weight > cc$cap), width = 0.68) +
    geom_hline(yintercept = cc$cap, linetype = "dashed", colour = ink) +
    geom_text(aes(label = percent(weight, 0.1)), hjust = -0.15, size = 3, colour = ink) +
    scale_fill_manual(values = c(`TRUE` = bad, `FALSE` = good), guide = "none") +
    coord_flip(clip = "off") +
    scale_x_discrete(labels = setNames(rows$label, as.character(rows$key))) +
    scale_y_continuous(labels = percent_format(accuracy = 1),
                       expand = expansion(mult = c(0, 0.16))) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Dashed line is your ", percent(cc$cap, 1),
                           " limit. Red is over it.\n",
                           "The bottom bar is every holding that moves with ",
                           "nothing else you own.")) +
    theme(plot.margin = margin(6, 26, 6, 6))
} else blank("not computable")
```

## Row {height="28%"}

```{r}
#| title: "Every holding, worst first"
p <- tbl(d$positions)
sm <- tbl(d$mix$detail)
p$moves_with <- NA_character_
if (nrow(sm) && "sector" %in% names(sm))
  p$moves_with <- sm$sector[match(p$symbol, sm$symbol)]
p <- p |> transmute(Symbol = symbol,
                    `Moves with` = moves_with,
                    Value = value,
                    `Share of book` = weight,
                    `Gain or loss` = plpc,
                    `In dollars` = pl)
dark_dt(p, options = list(pageLength = 12, dom = "ftip")) |>
  formatCurrency("Value", digits = 0) |>
  formatCurrency("In dollars", digits = 0) |>
  formatPercentage("Share of book", 2) |>
  formatPercentage("Gain or loss", 1) |>
  formatStyle("Gain or loss", color = styleInterval(0, c(bad, good)), fontWeight = "bold")
```

# Trades

## Row {height="12%"}

```{r}
#| content: valuebox
#| title: "Orders sent, last 90 days"
o <- tbl(d$orders)
list(icon = "send", color = "light", value = nrow(o))
```

```{r}
#| content: valuebox
#| title: "Filled"
o <- tbl(d$orders)
list(icon = "check2-circle", color = "light",
     value = if (nrow(o)) sum(o$status == "filled") else 0)
```

```{r}
#| content: valuebox
#| title: "Finished trades"
rt <- tbl(d$roundtrips)
list(icon = "arrow-left-right", color = "light", value = nrow(rt))
```

```{r}
#| content: valuebox
#| title: "Money made on finished trades"
rt <- tbl(d$roundtrips)
list(icon = "cash-stack",
     color = if (!nrow(rt)) "secondary" else tone(sum(rt$pl)),
     value = if (!nrow(rt)) "none yet" else usd(sum(rt$pl)))
```

```{r}
#| content: valuebox
#| title: "Of those, how many won"
rt <- tbl(d$roundtrips)
list(icon = "trophy",
     color = "light",
     value = if (!nrow(rt)) "n/a"
             else paste0(sum(rt$pl > 0), " of ", nrow(rt)))
```

```{r}
#| content: valuebox
#| title: "Typical days held"
rt <- tbl(d$roundtrips)
list(icon = "hourglass-split", color = "light",
     value = if (!nrow(rt)) "n/a" else sprintf("%.1f", median(rt$held_days)))
```

## Row {height="30%"}

### Column {width="60%"}

```{r}
#| title: "When each stock was bought and when it was let go"
#| fig-width: 7.2
#| fig-height: 9
o <- tbl(d$orders)
if (nrow(o)) {
  f <- o |> filter(status == "filled", !is.na(filled_at)) |>
    mutate(t = as.POSIXct(substr(filled_at, 1, 19), format = "%Y-%m-%dT%H:%M:%S",
                          tz = "America/New_York"))
  span <- f |> group_by(symbol) |>
    summarise(first = min(t), last = max(t),
              open = !any(side == "sell"), .groups = "drop") |>
    arrange(first) |> mutate(symbol = factor(symbol, levels = symbol))
  f$symbol <- factor(f$symbol, levels = levels(span$symbol))
  now <- as.POSIXct(substr(m$generated_at, 1, 19), format = "%Y-%m-%dT%H:%M:%S",
                    tz = "America/New_York")
  ggplot() +
    geom_segment(data = span,
                 aes(y = symbol, yend = symbol, x = first,
                     xend = ifelse(open, now, last)),
                 colour = grid, linewidth = 1.6) +
    geom_point(data = f, aes(t, symbol, colour = side, size = notional), alpha = 0.95) +
    scale_colour_manual(values = c(buy = accent, sell = warn), name = NULL,
                        labels = c(buy = "bought", sell = "sold")) +
    scale_size_continuous(range = c(0.9, 3.4), guide = "none") +
    labs(x = NULL, y = NULL,
         subtitle = paste0("One line per stock, running from its first purchase to its\n",
                           "sale, or to now if we still hold it. Dot size is the size\n",
                           "of the order in dollars.")) +
    theme(legend.position = "top",
          axis.text.y = element_text(size = 6.4, colour = mute))
} else blank("no orders in the last 90 days")
```

### Column {width="40%"}

```{r}
#| title: "What each finished trade made, and how long it was held"
rt <- tbl(d$roundtrips)
if (nrow(rt)) {
  rt <- rt |> mutate(win = pl > 0)
  ggplot(rt, aes(held_days, plpc, colour = win, size = abs(pl))) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    geom_point(alpha = 0.9) +
    scale_colour_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_size_continuous(range = c(1.4, 6), guide = "none") +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = "days the stock was held", y = NULL,
         subtitle = paste0("Each dot is one closed trade. Above the line it made money.\n",
                           "Dot size is the size of the gain or loss in dollars.\n",
                           "The strategy sells on a weekly schedule, not on a target,\n",
                           "so the holding times cluster around seven days."))
} else blank("nothing has been bought and sold yet")
```

## Row {height="34%" .tabset}

```{r}
#| title: "Finished trades"
rt <- tbl(d$roundtrips)
if (nrow(rt)) {
  x <- rt |> arrange(desc(sold_at)) |>
    transmute(Symbol = symbol,
              Bought = when(bought_at, 16),
              Sold = when(sold_at, 16),
              `Days held` = held_days,
              `Bought at` = buy_price, `Sold at` = sell_price,
              `Gain or loss` = plpc, `In dollars` = pl)
  dark_dt(x, options = list(pageLength = 12, dom = "ftip")) |>
    formatCurrency(c("Bought at", "Sold at"), digits = 2) |>
    formatCurrency("In dollars", digits = 0) |>
    formatPercentage("Gain or loss", 2) |>
    formatStyle("Gain or loss", color = styleInterval(0, c(bad, good)), fontWeight = "bold")
} else htmltools::HTML("<p>Nothing has been bought and sold yet.</p>")
```

```{r}
#| title: "Every order, newest first"
o <- tbl(d$orders)
if (nrow(o)) {
  x <- o |> arrange(desc(coalesce(filled_at, submitted_at))) |>
    transmute(Symbol = symbol,
              Side = side, Status = status,
              Sent = when(submitted_at),
              Filled = when(filled_at),
              Shares = qty, Price = price, Dollars = notional,
              `Minutes after the bell` = from_open,
              `Seconds to fill` = latency_s)
  dark_dt(x, options = list(pageLength = 15, dom = "ftip")) |>
    formatCurrency(c("Price"), digits = 2) |>
    formatCurrency("Dollars", digits = 0) |>
    formatRound("Shares", 3) |>
    formatStyle("Side", color = styleEqual(c("buy", "sell"), c(accent, warn)),
                fontWeight = "bold") |>
    formatStyle("Status", color = styleEqual(c("filled", "canceled", "rejected"),
                                             c(good, mute, bad)))
} else htmltools::HTML("<p>No orders in the last ninety days.</p>")
```

```{r}
#| title: "Everything that happened, in order"
tl <- tbl(d$timeline)
if (nrow(tl)) {
  x <- tl |> arrange(desc(t)) |>
    transmute(When = when(t),
              What = label, Detail = detail, Kind = kind)
  dark_dt(x, options = list(pageLength = 20, dom = "ftip")) |>
    formatStyle("Kind", color = styleEqual(
      c("buy", "sell", "rebalance", "report", "tick"),
      c(accent, warn, "#bc8cff", mute, good)))
} else htmltools::HTML("<p>Nothing recorded yet.</p>")
```

## Row {height="24%"}

### Column {width="55%"}

```{r}
#| title: "Cost per trade, each rebalance, against what we assumed"
s <- tbl(d$slippage)
if (nrow(s)) {
  s <- s |> mutate(cycle = as.Date(cycle))
  ggplot(s, aes(cycle)) +
    annotate("rect", xmin = min(s$cycle) - 1, xmax = max(s$cycle) + 1,
             ymin = s$model_low[1], ymax = s$model_high[1], fill = good, alpha = 0.16) +
    geom_segment(aes(xend = cycle, y = 0, yend = mean_bp), colour = grid) +
    geom_point(aes(y = mean_bp, colour = mean_bp > model_high), size = 4) +
    geom_point(aes(y = median_bp), shape = 21, fill = card, colour = ink, size = 2.6) +
    geom_text(aes(y = mean_bp, label = sprintf("%.1f", mean_bp)), vjust = -1.2,
              size = 3, colour = ink) +
    scale_colour_manual(values = c(`TRUE` = bad, `FALSE` = good), guide = "none") +
    labs(x = NULL, y = "basis points per fill",
         subtitle = paste0("Filled dot is the average, hollow dot the typical trade.\n",
                           "Green band is the 5 to 10 basis points we assumed. ",
                           "One basis point\nis a hundredth of one percent."))
} else blank("no trades yet")
```

### Column {width="45%"}

```{r}
#| title: "What time of day the orders actually filled"
o <- tbl(d$orders)
f <- if (nrow(o)) o |> filter(status == "filled", !is.na(from_open)) else o
if (nrow(f)) {
  ggplot(f, aes(from_open, fill = side)) +
    annotate("rect", xmin = -Inf, xmax = 15, ymin = 0, ymax = Inf,
             fill = bad, alpha = 0.14) +
    geom_histogram(binwidth = 10, colour = card, linewidth = 0.2) +
    scale_fill_manual(values = c(buy = accent, sell = warn), name = NULL,
                      labels = c(buy = "bought", sell = "sold")) +
    labs(x = "minutes after the 9:30 opening bell", y = "orders",
         subtitle = paste0("The red strip is the first fifteen minutes, where the gap\n",
                           "between what buyers offer and sellers ask is widest and\n",
                           "trading costs most. Orders sent overnight all land there.")) +
    theme(legend.position = "top")
} else blank("no fills yet")
```

# Markets

## Row {height="34%"}

```{r}
#| title: "How the big markets and every sector have moved"
ms <- d$markets$series
if (length(ms)) {
  rows <- lapply(names(ms), function(k) {
    x <- ms[[k]]
    data.frame(Symbol = k, Name = x$name %||% k, Role = x$role,
               Last = x$last %||% NA_real_,
               Today = x$day %||% NA_real_, Week = x$w1 %||% NA_real_,
               Month = x$m1 %||% NA_real_, `Three months` = x$m3 %||% NA_real_,
               `Six months` = x$m6 %||% NA_real_, Year = x$y1 %||% NA_real_,
               RSI = x$rsi %||% NA_real_, MACD = x$macd_state,
               Held = x$held, check.names = FALSE, stringsAsFactors = FALSE)
  })
  tb <- bind_rows(rows) |>
    filter(Role %in% c("index", "sector")) |>
    arrange(desc(Month)) |>
    mutate(MACD = ifelse(MACD == "above", "rising", "falling"),
           Held = ifelse(Held, "yes", ""))
  cols <- c("Today", "Week", "Month", "Three months", "Six months", "Year")
  dark_dt(tb |> select(-Role),
          options = list(pageLength = 16, dom = "t", scrollX = TRUE)) |>
    formatCurrency("Last", digits = 2) |>
    formatPercentage(cols, 1) |>
    formatRound("RSI", 0) |>
    formatStyle(cols, color = styleInterval(0, c(bad, good))) |>
    formatStyle("MACD", color = styleEqual(c("rising", "falling"), c(good, bad)))
} else htmltools::HTML("<p>No market data.</p>")
```

::: {.card title="Reading this table"}
Each row is a fund that stands for one slice of the market: SPY is the whole US
market, QQQ the big technology names, IWM the small companies, GLD gold, TLT
long government bonds, and every XL- fund one industry. The percentage columns
are price change over that stretch, so **Month** means "up or down this much
since a month ago". **RSI** is a 0-100 speed gauge: above 70 the price has run
up fast and often pauses, below 30 it has fallen fast. **MACD** compares a fast
average of the price against a slow one; *rising* means the fast one is above,
which is the trend-following read that the book's own signal uses.
:::

## Row {height="52%" .tabset}

```{r}
#| output: asis
ms <- d$markets$series

# One drawing routine, called once per tab. Three stacked panels sharing an
# x axis: the candles with three trend averages, then MACD, then volume. The
# MACD is the same 12/26/9 the research chapters use, so a number here and a
# number in a notebook mean the same thing.
draw_symbol <- function(sym) {
  x <- ms[[sym]]
  b <- tbl(x$bars)
  if (!nrow(b)) return(blank(paste("no bars for", sym)))
  b <- b |> mutate(date = as.Date(date), up = close >= open)
  cndl <- ggplot(b, aes(date)) +
    geom_linerange(aes(ymin = low, ymax = high, colour = up), linewidth = 0.3) +
    geom_linerange(aes(ymin = pmin(open, close), ymax = pmax(open, close),
                       colour = up), linewidth = 1.5) +
    geom_line(aes(y = ema20), colour = accent, linewidth = 0.45, na.rm = TRUE) +
    geom_line(aes(y = ema50), colour = warn, linewidth = 0.45, na.rm = TRUE) +
    geom_line(aes(y = ema200), colour = "#bc8cff", linewidth = 0.5, na.rm = TRUE) +
    scale_colour_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         title = paste0(sym, if (!identical(x$name, sym)) paste0("   ", x$name) else "",
                        "    $", formatC(x$last, format = "f", digits = 2),
                        "    today ", pct(x$day %||% NA, 1),
                        ", month ", pct(x$m1 %||% NA, 1),
                        ", year ", pct(x$y1 %||% NA, 1)),
         subtitle = paste0("Each candle is one day: the thin line is the day's full range,\n",
                           "the thick body runs from the opening price to the close.\n",
                           "Green closed up, red closed down. The three curves are average\n",
                           "prices over the last 20 days (blue), 50 (amber) and 200 (violet).",
                           if ((x$clipped %||% 0) > 0)
                             paste0("\n", x$clipped, " day's range came back from the feed with a",
                                    " misplaced decimal\npoint and was pulled in to that day's",
                                    " opening and closing price.")
                           else "")) +
    theme(axis.text.x = element_blank())

  macd <- ggplot(b, aes(date)) +
    geom_col(aes(y = hist, fill = hist >= 0), width = 1, na.rm = TRUE) +
    geom_line(aes(y = macd), colour = accent, linewidth = 0.5, na.rm = TRUE) +
    geom_line(aes(y = signal), colour = warn, linewidth = 0.5, na.rm = TRUE) +
    geom_hline(yintercept = 0, colour = mute, linewidth = 0.3) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    labs(x = NULL, y = "MACD",
         subtitle = paste0("Blue is a fast price average minus a slow one; amber is a smoothed\n",
                           "copy of blue. Bars are the gap between them. Bars crossing above\n",
                           "zero is the classic buy signal, below zero the classic sell.")) +
    theme(axis.text.x = element_blank())

  vol <- ggplot(b, aes(date, volume, fill = up)) +
    geom_col(width = 1) +
    scale_fill_manual(values = c(`TRUE` = good, `FALSE` = bad), guide = "none") +
    scale_y_continuous(labels = label_number(scale_cut = cut_short_scale())) +
    labs(x = NULL, y = "shares traded",
         subtitle = "How many shares changed hands. A big move on thin volume is weaker.")

  cndl / macd / vol + plot_layout(heights = c(3, 1.5, 1))
}

# The symbols are not known until the data is read, so each tab is knitted as a
# child document. Printing chunk text would not work: by the time this runs,
# knitr has finished looking for chunks to execute.
picks <- unique(c(d$markets$watch, d$markets$focus))
picks <- picks[picks %in% names(ms)]
parts <- lapply(picks, function(s) {
  knitr::knit_child(
    text = c(sprintf("```{r}"),
             sprintf("#| title: \"%s\"", s),
             "#| fig-height: 7",
             "#| fig-width: 9.5",
             sprintf("draw_symbol(\"%s\")", s),
             "```"),
    envir = environment(), quiet = TRUE)
})
cat(unlist(parts), sep = "\n\n")
```

## Row {height="14%"}

::: {.card title="Which symbols appear here"}
The first five tabs are the markets the book measures itself against: **SPY**
the whole US market, **QQQ** the big technology names, **IWM** the small
companies, **GLD** gold and **TLT** long government bonds. The tabs after them
are the four holdings currently moving the account most, in either direction,
so they change as the book changes. Every sector fund is in the table above
even when it has no tab.
:::

# Rules

## Row {height="32%"}

```{r}
#| title: "Every safety rule, and whether it is holding right now"
g <- tbl(d$guards) |> transmute(Rule = name, `In plain words` = plain,
                               Status = state, `Right now` = value, Detail = detail)
dark_dt(g, options = list(dom = "t", pageLength = 20)) |>
  formatStyle("Status", fontWeight = "bold",
              color = styleEqual(c("OK", "DRIFT", "BREACH", "TRIPPED", "FIRING", "STOPPED"),
                                 c(good, warn, bad, bad, bad, bad)))
```

## Row {height="40%"}

### Column {width="55%"}

```{r}
#| title: "How often it actually rebalanced, against the seven days it intends"
cy <- d$cycles
ds <- as.Date(unlist(cy$dates))
if (length(ds) > 1) {
  gp <- data.frame(when = ds[-1], gap = as.numeric(diff(ds)))
  ggplot(gp, aes(when, gap)) +
    geom_hline(yintercept = 7, linetype = "dashed", colour = accent) +
    geom_col(aes(fill = gap > 7), width = 0.5) +
    geom_text(aes(label = paste0(gap, "d")), vjust = -0.6, size = 3, colour = ink) +
    scale_fill_manual(values = c(`TRUE` = warn, `FALSE` = good), guide = "none") +
    scale_y_continuous(expand = expansion(mult = c(0, 0.18))) +
    labs(x = NULL, y = "days since the one before",
         subtitle = paste0("Dashed line is the weekly cadence the evidence tested.\n",
                           "A bar above it is a cycle that ran late, which stretches\n",
                           "how long the trial takes to finish."))
} else blank("needs two rebalances before a gap exists")
```

### Column {width="45%"}

::: {.card title="How far through the test we are"}
```{r}
#| output: asis
cy <- d$cycles
cat(sprintf(
"This is a paper trial with one job: find out whether real trading costs match
what the strategy assumed. That takes about **%d clean weekly rebalances**, and
**%d** are done.

", cy$needed, cy$done))
n_late <- length(unlist(cy$late))
if (n_late > 0) {
  cat(sprintf("%d ran late. The longest gap between two was **%d days** against the
7 days the weekly cadence intends.\n\n", n_late, cy$worst_gap))
} else if (cy$done > 1) {
  cat("None have run late.\n\n")
} else {
  cat("Too few rebalances yet to say whether the cadence holds.\n\n")
}
cat("Until the trial finishes, nothing here says the strategy works with real
money. It says the plumbing does.\n")
```
:::

## Row {height="28%"}

::: {.card title="What the concentration bar means"}
```{r}
#| output: asis
cc <- d$concentration
if (isTRUE(cc$available)) {
  cat(sprintf(
"The biggest group of stocks that move together is **%d of the %d holdings**, worth
**%s of the money**. Your rules cap any such group at %s.

Momentum concentrates on purpose: last year's winners are last year's winning
industry. That is why the book can lose six percent in a week the market barely
moves, and win it back the next day. Both are the same fact.

Right now **%d holding%s sit%s over the cap**, worst is %s at %s.\n\n",
    cc$biggest_group_names, h$positions, percent(cc$biggest_group_weight, 0.1),
    percent(cc$cap, 1), cc$over_cap, ifelse(cc$over_cap == 1, "", "s"),
    ifelse(cc$over_cap == 1, "s", ""), cc$worst_local_symbol,
    percent(cc$worst_local_weight, 0.1)))
}
```
:::

# History

## Row {height="40%"}

### Column {width="60%"}

```{r}
#| title: "What every past run of this page reported"
ar <- tbl(d$archive)
if (nrow(ar) > 1) {
  ar <- ar |> mutate(t = as.POSIXct(substr(generated_at, 1, 19),
                                    format = "%Y-%m-%dT%H:%M:%S",
                                    tz = "America/New_York"))
  ggplot(ar, aes(t, equity)) +
    geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
    geom_line(colour = accent, linewidth = 0.7) +
    geom_point(colour = accent, size = 1.4) +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Each dot is one refresh of this dashboard, stamped when it\n",
                           "ran. It is the page's memory of itself: if a figure here ever\n",
                           "disagrees with what an earlier run said, this is where that\n",
                           "shows up."))
} else blank("this is the first run kept in the archive")
```

### Column {width="40%"}

```{r}
#| title: "What each written report claimed at the time"
rp <- tbl(d$reports)
if (nrow(rp) > 1) {
  rp <- rp |> filter(!is.na(equity)) |>
    mutate(t = as.POSIXct(paste(date, time), format = "%Y-%m-%d %H:%M",
                          tz = "America/New_York"))
  ggplot(rp, aes(t, equity)) +
    geom_hline(yintercept = 100000, linetype = "dotted", colour = mute) +
    geom_step(colour = warn, linewidth = 0.7) +
    geom_point(colour = warn, size = 2) +
    scale_y_continuous(labels = dollar_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("The account value stated in each daily markdown report\n",
                           "under outputs/AA-evals/. Two lines that should agree:\n",
                           "this one and the one to its left."))
} else blank("fewer than two reports written so far")
```

## Row {height="30%"}

```{r}
#| title: "The written reports, newest first"
rp <- tbl(d$reports)
if (nrow(rp)) {
  x <- rp |> arrange(desc(date), desc(time)) |>
    transmute(Date = date, Time = time,
              `Account value it reported` = equity,
              `Change since live it reported` = since_live,
              File = file, KB = kb)
  dark_dt(x, options = list(pageLength = 12, dom = "ftip")) |>
    formatCurrency("Account value it reported", digits = 0) |>
    formatPercentage("Change since live it reported", 2) |>
    formatStyle("Change since live it reported",
                color = styleInterval(0, c(bad, good)))
} else htmltools::HTML("<p>No reports written yet.</p>")
```

## Row {height="30%"}

```{r}
#| title: "Every refresh of this page that was kept"
ar <- tbl(d$archive)
if (nrow(ar)) {
  x <- ar |> arrange(desc(generated_at)) |>
    transmute(When = when(generated_at),
              `Account value` = equity,
              `Since live` = since_live,
              Holdings = positions,
              `Cash share` = cash_pct,
              `Below its peak` = from_peak,
              `Cycles done` = cycles_done,
              `Rules not OK` = vapply(guards_bad, function(v)
                if (length(v)) paste(v, collapse = ", ") else "none", character(1)),
              File = file)
  dark_dt(x, options = list(pageLength = 12, dom = "ftip")) |>
    formatCurrency("Account value", digits = 0) |>
    formatPercentage(c("Since live", "Cash share", "Below its peak"), 2) |>
    formatStyle("Since live", color = styleInterval(0, c(bad, good))) |>
    formatStyle("Rules not OK", color = styleEqual("none", good))
} else htmltools::HTML("<p>Nothing archived yet.</p>")
```
