---
title: "Swing trader"
format:
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
    theme: cosmo
    nav-buttons:
      - icon: github
        href: https://github.com/seamusrobertmurphy/swing-trader
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(jsonlite); library(ggplot2); library(dplyr); library(scales); library(DT)

# Find the repo root by walking up until inputs/ appears, so this renders the
# same from the repo root, from dashboard/, or from anywhere a scheduler puts
# its working directory. DAYTRADER_DATA overrides it outright.
find_repo <- function(start = getwd()) {
  p <- normalizePath(start, mustWork = FALSE)
  for (i in 1:6) {
    if (dir.exists(file.path(p, "inputs"))) return(p)
    parent <- dirname(p); if (parent == p) break; p <- parent
  }
  stop("cannot locate the repo root from ", start)
}
data_path <- Sys.getenv("DAYTRADER_DATA",
                        file.path(find_repo(), "outputs", "dashboard", "data.json"))
if (!file.exists(data_path))
  stop("no data at ", data_path, " -- run: .venv/bin/python inputs/dashboard_data.py")
d <- fromJSON(data_path, simplifyVector = TRUE)
if (!length(d$headline)) stop("data.json has no headline block; the emitter failed")

h <- d$headline; m <- d$meta

pct  <- function(x, dp = 2) sprintf(paste0("%+.", dp, "f%%"), 100 * x)
usd  <- function(x) paste0("$", formatC(x, format = "f", big.mark = ",", digits = 0))
good <- "#1a7f4e"; bad <- "#b3261e"; warn <- "#a1650a"; ink <- "#1f2328"
tone <- function(x) if (is.na(x)) "secondary" else if (x >= 0) "success" else "danger"

theme_book <- theme_minimal(base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold", size = 12),
        plot.subtitle = element_text(colour = "grey35", size = 10),
        axis.title = element_text(colour = "grey35", size = 9))
```

# Where the money is

## Row {height="18%"}

```{r}
#| content: valuebox
#| title: "Account value"
list(icon = "wallet2", color = tone(h$since_live),
     value = usd(h$equity))
```

```{r}
#| content: valuebox
#| title: "Since it went live"
list(icon = if (h$since_live >= 0) "graph-up" else "graph-down",
     color = tone(h$since_live), value = pct(h$since_live))
```

```{r}
#| content: valuebox
#| title: "The market, same days"
list(icon = "bank", color = "light",
     value = if (is.null(h$spy_since_live)) "n/a" else pct(h$spy_since_live))
```

```{r}
#| content: valuebox
#| title: "Cost per trade vs the 5-10 assumed"
list(icon = "cash-coin",
     color = if (!length(d$slippage)) "secondary"
             else if (tail(d$slippage$mean_bp, 1) <= 10) "success" else "danger",
     value = if (!length(d$slippage)) "no trades"
             else paste0(sprintf("%.1f", tail(d$slippage$mean_bp, 1)), " bp"))
```

```{r}
#| content: valuebox
#| title: "Clean cycles done"
list(icon = "arrow-repeat",
     color = if (d$cycles$done >= d$cycles$needed) "success" else "warning",
     value = paste0(d$cycles$done, " of ", d$cycles$needed))
```

## Row {height="12%"}

::: {.card title="What this page is"}
**This is fake money.** It is a paper account and the switch that would let it
spend real money is off.

`r m$mark_note` Marked `r m$generated_at_pretty`.
The book has been running `r m$sessions` trading sessions.
Was this move within expectations? **`r if (h$within_expectations) "Yes" else "No"`** —
the plan expected swings of about `r sprintf("%.1f%%", 100*h$expected_swing)` over
that stretch, and this is `r sprintf("%.1f", abs(h$sigmas))` times that.
:::

## Row {height="45%"}

### Column {width="62%"}

```{r}
#| title: "The book against the market, both starting at $100,000"
eq <- d$equity_curve |> mutate(date = as.Date(date), who = "The book")
bm <- if (length(d$benchmark$series)) {
  d$benchmark$series |> mutate(date = as.Date(date),
                              who = paste0("The market (", d$benchmark$symbol, ")"))
} else eq[0, ]
both <- bind_rows(eq, bm)

ggplot(both, aes(date, equity, colour = who)) +
  geom_hline(yintercept = 100000, linetype = "dotted", colour = "grey55") +
  geom_line(linewidth = 0.9) +
  geom_point(data = filter(both, date == max(date)), size = 2) +
  scale_colour_manual(values = setNames(c(ink, "grey60"), unique(both$who))) +
  scale_y_continuous(labels = dollar_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, colour = NULL,
       subtitle = "Dotted line is the starting stake. Above it is a profit.") +
  theme_book + theme(legend.position = "top")
```

### Column {width="38%"}

```{r}
#| title: "Is it one bet or fifty?"
cc <- d$concentration
if (isTRUE(cc$available)) {
  g <- cc$groups |> mutate(rank = row_number(),
                           label = paste0(n, ifelse(n == 1, " stock", " stocks")))
  ggplot(g, aes(reorder(label, weight), weight)) +
    geom_col(fill = ifelse(g$weight > cc$cap, bad, good), width = 0.7) +
    geom_hline(yintercept = cc$cap, linetype = "dashed", colour = ink) +
    annotate("text", x = 0.8, y = cc$cap, vjust = -0.7, hjust = 0, size = 3.1,
             colour = ink, label = paste0("your ", percent(cc$cap, 1), " limit")) +
    coord_flip() +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(x = NULL, y = NULL,
         subtitle = paste0("Each bar is a group of stocks that move together.\n",
                           "Red means the group is bigger than your rules allow.")) +
    theme_book
} else {
  ggplot() + annotate("text", 0, 0, label = "not computable") + theme_void()
}
```

## Row {height="25%"}

::: {.card title="What the concentration bar means"}
```{r}
#| output: asis
cc <- d$concentration
if (isTRUE(cc$available)) {
  cat(sprintf(
"The biggest group of stocks that move together is **%d of the %d holdings**, worth
**%s of the money**. Your rules cap any such group at %s.

Momentum concentrates on purpose: last year's winners are last year's winning
industry. That is why the book can lose six percent in a week the market barely
moves, and win it back the next day. Both are the same fact.

Right now **%d holding%s sit%s over the cap**, worst is %s at %s.\n\n",
    cc$biggest_group_names, h$positions, percent(cc$biggest_group_weight, 0.1),
    percent(cc$cap, 1), cc$over_cap, ifelse(cc$over_cap == 1, "", "s"),
    ifelse(cc$over_cap == 1, "s", ""), cc$worst_local_symbol,
    percent(cc$worst_local_weight, 0.1)))
}
```
:::

# What it costs to trade

## Row {height="50%"}

```{r}
#| title: "Cost per trade, each rebalance, against what we assumed"
if (length(d$slippage)) {
  s <- d$slippage |> mutate(cycle = as.Date(cycle))
  ggplot(s, aes(cycle)) +
    annotate("rect", xmin = min(s$cycle) - 1, xmax = max(s$cycle) + 1,
             ymin = s$model_low[1], ymax = s$model_high[1],
             fill = good, alpha = 0.14) +
    geom_segment(aes(xend = cycle, y = 0, yend = mean_bp), colour = "grey70") +
    geom_point(aes(y = mean_bp, colour = mean_bp > model_high), size = 4) +
    geom_point(aes(y = median_bp), shape = 21, fill = "white", size = 2.6) +
    geom_text(aes(y = mean_bp, label = sprintf("%.1f", mean_bp)),
              vjust = -1.1, size = 3.3) +
    scale_colour_manual(values = c(`TRUE` = bad, `FALSE` = good), guide = "none") +
    labs(x = NULL, y = "basis points per fill",
         subtitle = paste0("Filled dot is the average, hollow dot the typical trade.\n",
                           "Green band is the 5 to 10 basis points we assumed. ",
                           "One basis point is a hundredth of one percent.")) +
    theme_book
} else {
  ggplot() + annotate("text", 0, 0, label = "no trades yet") + theme_void()
}
```

## Row {height="50%"}

::: {.card title="The most recent rebalance"}
```{r}
#| output: asis
if (!length(d$slippage)) {
  cat("Nothing has traded in the last sixty days, so there is nothing to measure.\n")
} else {
  s   <- tail(d$slippage, 1)
  dol <- function(x) paste0("$", formatC(x, format = "f", digits = 0, big.mark = ","))
  cat(sprintf(
"On **%s** it made **%d fills**, costing **%.1f basis points on average** and
**%.1f for the typical one**. In money, %s on %s traded.\n\n",
    format(as.Date(s$cycle), "%-d %B"), s$fills, s$mean_bp, s$median_bp,
    dol(s$dollars), dol(s$notional)))

  # The verdict is derived, never asserted: the page must not keep repeating a
  # diagnosis that was true of one cycle after later cycles have moved on.
  if (s$at_open > 0) {
    cat(sprintf(
"**%d of those %d fills landed in the first fifteen minutes of the day.** That
is almost certainly the cause. The opening bell has the widest gap between what
buyers offer and sellers ask, and prices move fastest. Orders sent to a shut
exchange all execute the instant it opens, so an overnight submission lands
exactly there.\n\n", s$at_open, s$fills))
  } else {
    cat("None of those fills landed in the opening minutes, which is where the
cost is. They were spread through the session, as intended.\n\n")
  }

  if (s$mean_bp > s$model_high) {
    cat(sprintf("That is above the %.0f to %.0f basis points the strategy assumed, so
this cycle does not support the assumption.\n", s$model_low, s$model_high))
  } else {
    cat(sprintf("That is within the %.0f to %.0f basis points the strategy assumed.\n",
                s$model_low, s$model_high))
  }

  if (nrow(as.data.frame(d$slippage)) > 1) {
    all <- as.data.frame(d$slippage)
    cat(sprintf("\nAcross all %d rebalances so far the average is %.1f basis points,
and %d of them came in at or under the assumption.\n",
      nrow(all), mean(all$mean_bp), sum(all$mean_bp <= all$model_high)))
  }
}
```
:::

# What we own

## Row

```{r}
#| title: "Every holding, worst first"
p <- d$positions |>
  transmute(Symbol = symbol,
            Value = value,
            `Share of book` = weight,
            `Gain or loss` = plpc,
            `In dollars` = pl)
datatable(p, rownames = FALSE, options = list(pageLength = 15, dom = "tip"),
          class = "compact stripe hover") |>
  formatCurrency("Value", digits = 0) |>
  formatCurrency("In dollars", digits = 0) |>
  formatPercentage("Share of book", 2) |>
  formatPercentage("Gain or loss", 1) |>
  formatStyle("Gain or loss",
              color = styleInterval(0, c("#b3261e", "#1a7f4e")),
              fontWeight = "bold")
```

# Are the rules holding

## Row

```{r}
#| title: "Every safety rule, and whether it is holding right now"
g <- d$guards |> transmute(Rule = name, `In plain words` = plain,
                          Status = state, `Right now` = value, Detail = detail)
datatable(g, rownames = FALSE, options = list(dom = "t", pageLength = 20),
          class = "compact stripe") |>
  formatStyle("Status", fontWeight = "bold",
              color = styleEqual(c("OK", "DRIFT", "BREACH", "TRIPPED", "FIRING"),
                                 c("#1a7f4e", "#a1650a", "#b3261e", "#b3261e", "#b3261e")))
```

## Row {height="30%"}

::: {.card title="How far through the test we are"}
```{r}
#| output: asis
cy <- d$cycles
cat(sprintf(
"This is a paper trial with one job: find out whether real trading costs match
what the strategy assumed. That takes about **%d clean weekly rebalances**, and
**%d** are done.

", cy$needed, cy$done))
n_late <- length(cy$late)
if (n_late > 0) {
  cat(sprintf("%d ran late. The longest gap between two was **%d days** against the
7 days the weekly cadence intends.\n\n", n_late, cy$worst_gap))
} else if (cy$done > 1) {
  cat("None have run late.\n\n")
} else {
  cat("Too few rebalances yet to say whether the cadence holds.\n\n")
}
cat("Until the trial finishes, nothing here says the strategy works with real
money. It says the plumbing does.\n")
```
:::
