---
title: "QUICKSTART"
author: "Murphy, S"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Environment setup

This workflow does not use AlpacaforR. That package breaks on R 4.3 and later
(length-2 `&&`, deprecated purrr internals). Instead we call the Alpaca REST API
directly through `httr2`, which is current and maintained. The logic lives in
`R/alpaca.R`; this document just drives it.

```{r packages}
for (p in c("httr2", "jsonlite")) {if (!requireNamespace(p, quietly = TRUE)) install.packages(p)}
source("R/alpaca.R")
```

### API keys

Store your keys once in your user `.Renviron`, then restart R. Open it with:

```{r edit-environ, eval=FALSE}
usethis::edit_r_environ()
```

Add these lines and save. The first two are all you need for paper trading.

```
ALPACA_API_KEY=your-paper-key
ALPACA_API_SECRET=your-paper-secret
ALPACA_BASE_URL=https://paper-api.alpaca.markets
LIVE_TRADING=false
```

Your existing `APCA-PAPER-KEY` and `APCA-PAPER-SECRET` names still work as a
fallback, so nothing breaks if you leave them. Keys live only in `.Renviron`,
never in this document or the repo.

### Confirm the connection

`alpaca_clock()` and `alpaca_account()` both require a valid key, so if these
return, your authentication works.

```{r connect}
alpaca_clock()
alpaca_account()
```

You should see your paper account with `paper = TRUE` and its practice equity.

### Place a paper order

This chunk is `eval=FALSE` so knitting the document never places an order. Run
it yourself in the console when you want to. It buys ten dollars of a stock at
market on the paper account, so it spends practice money only.

```{r paper-buy, eval=FALSE}
alpaca_paper_buy("AAPL", notional = 10)
```

If the market is closed the order queues and fills at the next open. That is
normal.

### Read the result back

```{r read-back, eval=FALSE}
alpaca_positions()
alpaca_orders(status = "all", limit = 10)
```

### What changed from the old QUICKSTART

`firstrun()` is gone. It failed on R 4.4 and was never needed: your keys load
from `.Renviron` on their own, which is why `account_config()` already returned
HTTP 200 for you. The hand-written keys passed to `firstrun` were also fake
placeholders that would have overwritten your real ones. Every function here is
in `R/alpaca.R`, short enough to read top to bottom and change yourself.
